---
title: "Post-precossing"
output: html_document
---
##Functions
```{r}
colorSomeCells<-function(clusterMatrix, coordsTable, cellsToColor){
  clusterMatrix$toColor=FALSE
  clusterMatrix[cellsToColor,which(colnames(clusterMatrix)=="toColor")]<-TRUE
  
  p1 <- ggplot()+
    geom_point(aes_string(x=colnames(coordsTable)[1],y=colnames(coordsTable)[2], colour=clusterMatrix$toColor), data=coordsTable, size=1) +
    scale_color_manual(values=c('TRUE'="orangered",'FALSE'="lightgray")) +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.text=element_text(size=12))
  
  return(p1)
}

```



```{r}
## Packages
library("tidyverse")
library("Seurat")
library("SingleCellExperiment")
library("scater")
library("data.table")
library("ggpubr")
library("gridExtra")
library("fitdistrplus") 
library("dplyr")
library("plyr")
library("caret")
library("openxlsx")
library("ggplot2")
library("tibble")
library("scran")
library("limma")
library("ggrepel")
library("intrinsicDimension")
library("tidyr")
library("purrr")
library("ggrepel")
library("clustree")
library("limma")
library("patchwork")
library("future")
library('RColorBrewer')

```


#Post-Processing

After Basic filtering of data we want to take a closer look at each cluster that and see where further processing is necessary 


## Loading the Seurat Object
```{r}
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM05")
FileName <- basename(getwd())


#Loading Seaurat object
seuratObj <- readRDS(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Hashing/SeuratObj_HTO_",FileName,".rds"))



```


##Making Subsets of the data
```{r}

# Subset: Removing the Negative and Doublets
# Only HTO.data doublets removed ---> scdblfinder doublets are still in the the seuratObj 
ncol(seuratObj)
seuratObjR <- subset(seuratObj,seuratObj@meta.data$HTO_GUESS != "Doublet" & seuratObj@meta.data$HTO_GUESS != "Negative")
ncol(seuratObjR)

Idents(seuratObjR) <- "HTO_GUESS"

PlotSeurat <- DimPlot(seuratObj, label=T, repel=T )+ggtitle(paste0("Graph ",FileName))
PlotSeuratR <- DimPlot(seuratObjR, label=T, repel=T)+ggtitle(paste0("Graph",FileName))

PlotSeurat
PlotSeuratR 

Idents(seuratObjR) <- "seurat_clusters"

PlotSeuratRClust <- DimPlot(seuratObjR, label=T, repel=T )+ggtitle(paste0("Graph ",FileName," Clusters"))
PlotSeuratRClust

```

## Manual Cluster selection of Whole cluster

Checking the Doublet count of Cluster 12/ Unknown cell type
Selection
```{r}
ClusterData <- seuratObj@meta.data
UMAPTable <-as.data.frame(seuratObj[['RNA_umap']]@cell.embeddings, stringsAsFactors = F)
#Color Cluster Number?
ColorIdent <- 18
wantedCells<-WhichCells(seuratObjR, idents = ColorIdent)
PrecentageDoublet <- (length(WhichCells(seuratObjR, expression = scDblFinder_class=="doublet", cells = wantedCells))/length(WhichCells(seuratObjR,wantedCells)))*100
PrecentageDoublet <- paste0(round(PrecentageDoublet,2),"%")
PrecentageDoublet
ClustRemoveMap2 <- colorSomeCells(ClusterData, UMAPTable, wantedCells)+ggtitle(paste0("Cluster ",ColorIdent, " = ",PrecentageDoublet," Doublets"))

ClustRemoveMap1
ClustRemoveMap2

```

## Checking Unknow/ Suspicious cells
```{r}
# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjR, expression = sctype_classification == " Basophil cell")
# Making a plot showcasing these genes


# Checking If its is Basophill Cells
PlotUnknown1 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Mcpt8","Fcer1a","Fcer1g","adt_CD49b"))
PlotUnknown1 <- PlotUnknown1 +plot_annotation(title = "Controling if Basophil cell")

# Chech if CDC1
PlotUnknown2 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Cd81","Gcsam","Xcr1","Irf8"))
PlotUnknown2 <- PlotUnknown2 +plot_annotation(title = "Controling if CDC1")

# Checking if its is CDC2
PlotUnknown3 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Sirpa","S100a4","Cd209a"))
PlotUnknown3 <- PlotUnknown3 +plot_annotation(title = "Controling if CDC2")

# Checking if Migratory CDC1 
PlotUnknown4 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Cd81","Gcsam","Laptm4b","Ncoa7","Ccr7"))
PlotUnknown4 <- PlotUnknown4 +plot_annotation(title = "Controling if Migartory CDC1")

# Checking if Plasmacytoid dendritic cells
PlotUnknown5 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Siglech","Tcf4","Ccr9","Bst2"))
PlotUnknown5 <- PlotUnknown5 +plot_annotation(title = "Controling if Plasmacytoid dendritic cells")

# Checking if Plasmacytoid dendritic cells
PlotUnknown6 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Mki67","Stmn1"))
PlotUnknown6 <- PlotUnknown6 +plot_annotation(title = "Controling if Proliferating DCs")


PlotUnknown1
PlotUnknown2
PlotUnknown3
PlotUnknown4
PlotUnknown5
PlotUnknown6

#  Basophill are in are unexpected position when clustering, When checked the appear to not be Basophills. When checked for other cell types no conclusif answer was found. Going Further I looked at the MARKER_RNA data of SAM05 and found for the cluster of Basophill no clear cell type thus these cell will be REMOVED. 
```



## Removing Selecetd cluster or cluster of choice

```{r}
# Remove Selected
# Cluster 15 and 18 100% doublets ---> Removed
#Basophill cells ---> Removed

#Remove specific cluster (Change idents to choose which cluster to remove)
 ClusterCellsRemove <- WhichCells(seuratObjR, idents = c(15,18))
 seuratObjR <- subset(seuratObjR, cells = ClusterCellsRemove, invert=TRUE)

# Remove cells that can't be identified
  ClusterCellsRemove <- WhichCells(seuratObjR, expression = sctype_classification == " Basophil cell")
 seuratObjR <- subset(seuratObjR, cells = ClusterCellsRemove, invert=TRUE)
 
DimPlot(seuratObjR, reduction = "RNA_umap", label = T, repel = T, label.size = 4)

```






#Annontation Post-Processing of seuratObjR
```{r}
 PostAnnotClust <- DimPlot(seuratObj, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells Before"))

 PostAnnotClustR <- DimPlot(seuratObjR, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells After"))
 
 PostAnnotClust
 PostAnnotClustR

```


# CDC1: Repeat the process for CDC1
```{r}
#Subset: Only CDC 1

ncol(seuratObjR)
# Previous mistake in annotation excel ---> need the whitspace for CDC1
seuratObjCDC1 <- subset(seuratObjR, seuratObjR$sctype_classification == " Dendritic cells 1"| seuratObjR$sctype_classification == "Migratory dendritic cells 1" | seuratObjR$sctype_classification == "Proliferating DCs")
ncol(seuratObjCDC1)

#active idents 
Idents(seuratObjCDC1) <- "sctype_classification"

PlotSeuratCDC1 <- DimPlot(seuratObjCDC1,)+ggtitle(paste0("Graph: ",FileName," Annotation CDC1s Before"))
PlotSeuratCDC1

```


#Cleaning Up far off cells and removing Migratory CDC2
```{r}
selected <- CellSelector(DimPlot(seuratObjCDC1))
```

```{r}
seuratObjCDC1 <- subset(seuratObjCDC1, cells = selected, invert=TRUE)

```


##Annontation Post-Processing of CDC1
```{r}

 PostAnnotClustCDC1 <- DimPlot(seuratObjCDC1, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle("CDC Final result")
 PostAnnotClustCDC1

```
# Final count of CDC1
```{r}
nCellsSeurat <- ncol(seuratObj)
nCellsCDC1 <- ncol(seuratObjCDC1)
PlotCD1 <- data.frame(
  ObjectName= c("Seuratobj cell count" ,"Final seuratObjCDC1 cell count"),
  Cells = c(nCellsSeurat,nCellsCDC1)
)

BarplotCDC1 <- ggbarplot(
  PlotVBO,
  x = "ObjectName",
  y = "Cells",
  label = TRUE,
  fill = "ObjectName",
  palette = c("steelblue", "tomato"),
)+
scale_y_continuous(
    breaks = seq(0, 14000, by = 2000)
  )+ggtitle("Remainig CDC1 cell count after post-processing")

BarplotCDC1

```
 


# Notes
```{r}

blurb = paste("\n   Notes for The Post-Processing of SAM05.\n",
         "
		- Most Doublets removed when removing HTO.Data
		
		- Cluster 15 ---> 100% Doublets ---> Removed
		
		- Cluster 18 ---> 100% Doublets ----> Removed
		
		- Basophill cells ---> Coudn't be identified ---> Removed
")
Notes <- ggplot() + 
  annotate("text", x = 4, y = 25, size=4, label = blurb) + 
  theme_void()
Notes

```

#Saving Object
```{r}
#Saving Object
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))

saveRDS(seuratObjR,paste0("SeuratObj_Post-Process_",FileName,".rds"))
saveRDS(seuratObjCDC1,paste0("SeuratObj_Post-Process_CDC1_",FileName,".rds"))

setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))
pdf(paste0("Graphs Post-Process_",FileName,".pdf"), width = 14,
  height = 10)

PlotSeurat 
PlotSeuratR 
PostAnnotClust 
PostAnnotClustR
ClustRemoveMap1
ClustRemoveMap2
PlotUnknown1
PlotUnknown2
PlotUnknown3
PlotUnknown4
PlotUnknown5
PlotUnknown6
if (exists("PlotUnknown")) {print(PlotUnknown)}
PlotSeuratCDC1
PostAnnotClustCDC1
BarplotCDC1
Notes
dev.off()


```


