---
title: "Hashing"
output: html_document
---
# Use Multiplex Demux

```{r}
## Packages
library("tidyverse")
library("Seurat")
library("SingleCellExperiment")
library("scater")
library("data.table")
library("ggpubr")
library("gridExtra")
library("fitdistrplus") 
library("dplyr")
library("plyr")
library("caret")
library("openxlsx")
library("ggplot2")
library("tibble")
library("scran")
library("limma")
library("ggrepel")
library("intrinsicDimension")
library("tidyr")
library("purrr")
library("ggrepel")
library("clustree")
library("limma")
library("patchwork")
library("future")
library('RColorBrewer')

```




#Hashing Loading in HTO matrix

```{r}
#Load Seurat object
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM05")
FileName <- basename(getwd())

seuratObj <- readRDS(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/SeuratObj_Pre-Process_",FileName))

# Load HTO Matrix and add to the seuratobject
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM05")
FileName <- basename(getwd())
rawData <- Read10X("filtered_feature_bc_matrix")
rawDataHTO <- rawData[["Custom"]]

Cellsmin1Hash <- intersect(colnames(rawDataHTO), colnames(seuratObj))

rawDataHTO <- rawDataHTO[,Cellsmin1Hash]

#Filter the Seuratobject To remove Hashtag without cells
HTO_Above_0 <- rownames(rawDataHTO)[Matrix::rowSums(rawDataHTO > 0) > 0]
rawDataHTO <- rawDataHTO[HTO_Above_0, ]


seuratObj[["HTO"]] <- CreateAssayObject(counts = rawDataHTO[,colnames(seuratObj)] ,min.cells = 1)


```


## Normalize HTO data
```{r}
seuratObj <- NormalizeData(seuratObj, assay = "HTO", normalization.method = "CLR")

# To check HTO
# FeaturePlot(seuratObj, features="Hashtag1", pt.size=0.10,label.size = 8,order=T)
```

## Dimension reduction (VOOR OF NA DEMulitplexing)
```{r}

VariableFeatures(seuratObj, assay = "HTO") <- rownames(seuratObj[["HTO"]])

seuratObj <- ScaleData(seuratObj, assay = "HTO" )
seuratObj <- RunPCA(object = seuratObj, assay = "HTO", features = VariableFeatures(seuratObj, assay = "HTO"), 
                    npcs = nrow(seuratObj@assays$ADT), ndims.print = 1:5, nfeatures.print = 8,
                    reduction.name = "HTO_pca",reduction.key = "htoPC_")

Elbow <- ElbowPlot(seuratObj, reduction = "HTO_pca")
Elbow

seuratObj <- RunUMAP(seuratObj, dims = 1:10,assay = "HTO", reduction ="HTO_pca",
                       reduction.name = "HTO_umap", reduction.key = "HTOUMAP_")
# ???? Wat moet ik hier uit halen
DimPlot(seuratObj, reduction = "HTO_umap",label = T, repel = T, label.size = 4)
```
## Demultiplexing
```{r}
#SAM05 there are cell with no hashtags

seuratObj <- MULTIseqDemux(seuratObj, assay = "HTO", autoThresh = T,maxiter=5,qrange = seq(from = 0.1, to =  0.9, by =0.05))
```

## Creating Metadata (Provided by VIB)
```{r}
# creating of HTO.data, the metadata
HTO.data <- as.data.frame(t(as.matrix(GetAssayData(object = seuratObj, assay = "HTO", layer  = "counts")))) #hashcounts
HTO.data.raw <- HTO.data
features <- colnames(HTO.data.raw) #hashtags
HTO.data$maxHTO <- apply(HTO.data.raw,1,which.max) #max hash
HTO.data <- mutate(HTO.data,maxHTO=features[maxHTO])
HTO.data$maxval <- apply(HTO.data.raw,1,max)
sec.fun <- function(x){features[order(x)[length(x)-1]]}
secval.fun <- function(x){x[order(x)[length(x)-1]]}
HTO.data$secHTO <- apply(HTO.data.raw,1,sec.fun)
HTO.data$secval <- apply(HTO.data.raw,1,secval.fun)
HTO.data$nUMI <- seuratObj$nCount_RNA
HTO.data$nGene <- seuratObj$nFeature_RNA
HTO.data$cell <- rownames(HTO.data.raw)

#Multiplex Metadata
HTO.data$Multi_label <- seuratObj$MULTI_ID
HTO.data$Multi_glob <- seuratObj$MULTI_classification
HTO.data$Multi_class <- HTO.data$Multi_label
levels(HTO.data$Multi_class) <- ifelse(levels(HTO.data$Multi_class) %in% c("Doublet","Negative"),levels(seuratObj$MULTI_ID),"Singlet")
HTO.data$Multi_class <- factor(HTO.data$Multi_class,levels(HTO.data$Multi_class)[c(2,1,3)])


max.barplot <-   ggplot(HTO.data,aes(x=maxHTO)) +
  geom_bar(aes(y = (..count..)/sum(..count..)),fill = "#0073C2FF") + 
  scale_y_continuous(labels=scales::percent) +
  labs(y = "Percent", fill="class") +
  theme_bw() +
  theme(legend.position = "none", text = element_text(size=20)) +
  ggtitle("Cell frequencies per maximum Hashtag")  
max.barplot



```


## Visualization
```{r}
secmax_MultiLabel <- ggplot(HTO.data,aes(x = log2(maxval+1),y = log2(secval+1),color=Multi_label)) +
  geom_point(size=0.75) +
  geom_abline(slope = 1 ,color = "blue" ) +
  geom_abline(slope = 0.80 ,color = "red" ) +
  theme_bw() +
  theme(text = element_text(size=15)) +
  guides(colour = guide_legend(override.aes = list(size=3))) +
  facet_wrap(~maxHTO) +
  #scale_color_manual(values=c("firebrick", "coral","limegreen")) + #Doublet Negative Singlet
  ggtitle("Log2 counts per maximum and second largest value HTO: Multiseq_Demux")

secmax_MultiLabel
```



##NEEDED FOR HASHING COMPARISON
```{r}
# Vector needed
MULTI_ID <- HTO.data$Multi_label
# hash.ID ? NOT FOUND
# HTO_classification.global? NOT found



#png(filename = paste0(output.dir,"Plots/HTO/","08_umap_HTO_compare",".png"), width = 1500, height = 1000)

ggarrange(#DimPlot(seuratObj, reduction = "HTO_umap", group.by = "freemuxlet_guess", pt.size = 1)+ggtitle("Freemuxlet:label"),
  
  #DimPlot(seuratObj, reduction = "HTO_umap", group.by = "hash.ID", pt.size = 1)+ggtitle("HTOdemux:label"),
  DimPlot(seuratObj, reduction = "HTO_umap", group.by = "MULTI_ID", pt.size = 1)+ggtitle("Multiseq:label"),
  
  #DimPlot(seuratObj, reduction = "HTO_umap", group.by = "freemuxlet_type", pt.size = 1)+ggtitle("Freemuxlet:type"),

  #DimPlot(seuratObj, reduction = "HTO_umap", group.by = "HTO_classification.global", pt.size = 1)+ggtitle("HTOdemux:type"),
  ncol=3, nrow=2)
dev.off()


# PDF Version
#pdf(file =  paste0(output.dir,"Plots/HTO/","08_umap_HTO",".pdf"), width=10, height = 10)
# DimPlot(seuratObj, reduction = "HTO_umap", group.by = "freemuxlet_guess", pt.size = 1)+ggtitle("Freemuxlet:label")
#DimPlot(seuratObj, reduction = "HTO_umap", group.by = "hash.ID", pt.size = 1)+ggtitle("HTOdemux:label")
DimPlot(seuratObj, reduction = "HTO_umap", group.by = "MULTI_ID", pt.size = 1)+ggtitle("Multiseq:label")
# DimPlot(seuratObj, reduction = "HTO_umap", group.by = "freemuxlet_type", pt.size = 1)+ggtitle("Freemuxlet:type")
#DimPlot(seuratObj, reduction = "HTO_umap", group.by = "HTO_classification.global", pt.size = 1)+ggtitle("HTOdemux:type")
#dev.off()

```



```{r}
# Vector Needed for graph
PresentHashingAntibodies<-c("Hashtag1","Hashtag2",
                            "Hashtag3", "Hashtag5","Hastag6")
HTOCounts<-as.matrix((rowSums(as.matrix((seuratObj@assays$HTO@counts)))))
TrueDetectedAbs<-intersect(PresentHashingAntibodies, rownames(HTOCounts))


#pdf(file = paste0(output.dir,"Plots/HTO/Overview_HTO.pdf"), width = 10, height = 10)

# FeaturePlot(seuratObj, features="Hashtag1", pt.size=0.10,label.size = 8,order=T)
# FeaturePlot(seuratObj, features="Hashtag2", pt.size=0.10,label.size = 8,order=T)

# SAM05 geen Hastag6 in feature plot
FeaturePlot(seuratObj, features=(TrueDetectedAbs),ncol=2, pt.size=0.1, label.size = 8,order=T)


#DimPlot(seuratObj,group.by = "hash.ID", label = F, pt.size = 0.1) + ggtitle("HTOdemux")
#DimPlot(seuratObj,split.by = "hash.ID", group.by = "hash.ID", label = F, pt.size = 0.1, ncol = 2) + ggtitle("HTOdemux")

DimPlot(seuratObj,group.by = "MULTI_ID", label = F, pt.size = 0.1) + ggtitle("MULTIseqDemux")
DimPlot(seuratObj,split.by = "MULTI_ID", group.by = "MULTI_ID", label = F, pt.size = 0.1, ncol = 2) + ggtitle("MULTIseqDemux")

#DimPlot(seuratObj,group.by = "HTO_maxID", label = F, pt.size = 0.1) + ggtitle("MAX HTO count")
#DimPlot(seuratObj,split.by = "HTO_maxID", group.by = "HTO_maxID", label = F, pt.size = 0.1, ncol = 2) + #ggtitle("MAX HTO count")
dev.off()
```



### Fetch doublets from hashing ###
# -> uses Hashing data to find Doublets and Negatives
```{r}
## Create HTO.data
# get hashtags present
tags <- rownames(seuratObj@assays$HTO@data)
# get barcodes
barcodes <- colnames(seuratObj@assays$HTO@data)
# make data frame 
HTO.data <- as_tibble(t(seuratObj@assays$HTO@data))
HTO.data$barcodes <- barcodes

## Add column with the highest hashtag and its value
max.tags <- c()
for (barcode in HTO.data$barcodes){
  #print(names(which.max(HTO.data[,barcode])))
  highest.HTO <- names(which.max(HTO.data[HTO.data$barcodes == barcode,]))
  #seuratObj@meta.data[rownames(seuratObj@meta.data) == barcode,"maxHTO"] <- highest.HTO
  max.tags <- append(max.tags, highest.HTO)
  #print(rownames(HTO.data[HTO.data[[barcode]] == max(HTO.data[[barcode]]),])) # for the maximum value
}

# merge with HTO.data
HTO.data <- cbind(HTO.data,max.tags)
# get value of the max hashtag
HTO.data$max.HTO.val <- apply(HTO.data[,tags],1,max)

#View(HTO.data)

## Visualize Hashtag Expression levels
p <- ggplot(HTO.data, aes(x=max.tags, y=max.HTO.val, fill=max.tags)) +
  geom_boxplot() +
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme(
    legend.position="none",
    plot.title = element_text(size=18)
  ) +
  ggtitle("Check if expression levels are similar!") +
  xlab("") + theme_classic()
print(p)

```
## Create Hashtag.info table | Causes Near Crashes DONT USE
```{r}
############## NOTE : HEB DEZE CODE AANGEPAST #########################""
hashtag.info <- as_tibble(tags)
colnames(hashtag.info) <- "tag"
# Add quantile percentages for each hashtag
q.data <- tibble()
for (tag in tags){
  # get quantile distribution (MANUAL threshold)
  q <- quantile(HTO.data[HTO.data$max.tags == tag,tag],probs = seq(0, 1, by=0.01), names = T)
}

q
```

# Experession cutoff
```{r}
  # find expression level were to place cutoff for each hashtag
  # In the plots we should see 2 peaks and cut_off needs to be in the middle of those peaks
  # We also need to make sure we actually see those peaks! if not this method probably will not work
  df <- HTO.data[,c(tag,"max.tags")]
  # get density with good precision
  #d <- density(df[[tag]])
  #In case you need a higher "precision"
  d <- density(df[[tag]], n=1e4)
  
  #Two ways to get highest Peak
  #d$x[d$y==max(d$y)]  #Gives you all highest Peaks
  #d$x[which.max(d$y)] #Gives you the first highest Peak
  #3 ways to get all Peaks
  d$x[c(F, diff(diff(d$y)>=0)<0)] #This detects also a plateau
  #d$x[c(F, diff(sign(diff(d$y)))<0)]
  #d$x[which(diff(sign(diff(d$y)))<0)+1]
  
  #In case you also want the height of the peaks
  peak_positions <- data.frame(d[c("x", "y")])[c(F, diff(diff(d$y)>=0)<0),]
  colnames(peak_positions) <- c(tag,"density")
  # extract peaks
  x_first_peak <- peak_positions[1,tag]
  x_second_peak <- peak_positions[2,tag]
  y_first_peak <- peak_positions[1,"density"]
  y_second_peak <- peak_positions[2,"density"]
  
  # Find minimum between peaks
  MinYDensity <- min(d$y[d$x > x_first_peak & d$x < x_second_peak])
  index <- which(d$y == MinYDensity)
  # min_expr <- d$x[index] #removed by clint!!
  min_expr<-q_manual_clint[tag]  #Clint
```


```{r}
  ## Barplot
  barplot <- ggplot(df, aes(x = .data[[tag]], fill = max.tags)) +
  geom_histogram(position = "stack", bins = 75) +
  theme_classic(base_size = 20) + ggtitle(paste0("Normalised ",tag, " Expression in all Cells"))
  ## Densityplot
  densityplot <- ggplot(df, aes(x = .data[[tag]])) +
  geom_density()+
  geom_vline(linetype="dashed",xintercept = x_first_peak, color = "black") +
  geom_vline(linetype="dashed",xintercept = x_second_peak, color = "black") +
  geom_vline(linetype="dashed",xintercept = min_expr, color = "red") +
  theme_classic() + ggtitle(paste0("Normalised ",tag, " Expression in all Cells"))
  print(ggarrange(barplot,densityplot))
```

```{r}
  pdf(file =  paste0(output.dir,"Plots/HTO/","10_Cutoff_plots_clint_v2_",tag,".pdf"), width=10, height = 10)
  print(
    ggplot(df, aes(x = .data[[tag]], fill = max.tags)) +
      geom_histogram(aes(y = ..density..),position = "stack", bins = 20) +
      geom_density(aes(x = .data[[tag]], fill = NULL)) +
      geom_vline(linetype="longdash",xintercept = x_first_peak, color = "black") +
      geom_vline(linetype="longdash",xintercept = x_second_peak, color = "black") +
      geom_vline(linetype="solid",xintercept = min_expr, color = "red", size = 2) +
      scale_x_continuous(breaks=seq(0, 10, 0.5)) + #Clint
      theme_classic(base_size = 20) +  
      ggtitle(paste0("Normalised ",tag, " Expression in all Cells"))
    )
  dev.off()
```
  
  
  
  # Add automaticly found value to quantile range
  q["auto"] <- min_expr
  
  
  # Add information to tibble
  q.data <- rbind(q.data,as_tibble(as.list(q)))

}

## Added by Clint
## Sadly, too many peaks present in data for hashtag 7. Minimum between first two peaks is not a good cut-off!!
## Manually determined by the plots
tags <- rownames(seuratObj@assays$HTO@data)
q_manual_clint<-c(1.2,1.0,0.95,1.2,1.0,1.0) #1,2,3,4,5,6
names(q_manual_clint)<-tags[2:7]

# merge with hashtag.info
hashtag.info <- cbind(hashtag.info,q.data)

#View(hashtag.info)  
## get for each cell in HTO.data expression of lower x% of all the cells for each hashtag! if cell in lower x% foor all tags -> negative
#q.cutoff <- "10%"
# loop over all values in HTO.data
for (c in 1:nrow(HTO.data)){
  for (tag in tags){
    # check if value is lower then x% quantile for all tags
    if (HTO.data[[tag]][c] <= hashtag.info[hashtag.info$tag == tag,q.cutoff]){
      HTO.data[c,paste0(tag,"_neg")] <- T
    } else {
      HTO.data[c,paste0(tag,"_neg")] <- F
    }
  }
}
# get colnames of negatives
negatives_cols <- c()
for (tag in tags){
  negatives_cols <- append(negatives_cols,paste0(tag,"_neg"))
}
# loop over all negative columns to get all negatives in lower left corner aka all cells who fall below the lower quantile for all hashtags
HTO.data$negative <- apply(HTO.data[,negatives_cols], 1, all)
table(HTO.data$negative)

# check if a hashtag is above the minimum quantile for multiple hashtags -> these are doublets!
for (c in 1:nrow(HTO.data)){
  # fetch status for all hashtags
  status <- c()
  for (tag in tags){
    if (HTO.data[c,tag] >= hashtag.info[hashtag.info$tag == tag,q.cutoff]){
      status <- append(status,T)
    } else {status <- append(status,F)}
  }
  # check if it is positive for multiple hashtags if True add true to doublet column
  if (sum(status==TRUE) > 1){
    HTO.data[c,"doublet"] <- T
  } else {HTO.data[c,"doublet"] <- F}
}
table(HTO.data$doublet)

## Merge DoubletFinder Information with HTO.data
# add barcode names to metadata
seuratObj@meta.data$barcodes <- rownames(seuratObj@meta.data)
# Fetch doublet information from DoubletFinder and the barcodes
data <- as_tibble(seuratObj@meta.data[,c("barcodes","DFPrediction")]) #Clint
# merge
HTO.data <- merge(HTO.data,data)

### ASSIGN TOOL RESULTS ###
# HTO cutoff method
HTO.data$HTO_Results <- NA
HTO.data[,"HTO_Results"] <- HTO.data$max.tags
HTO.data[HTO.data$negative == T,"HTO_Results"] <- "Negative"
HTO.data[HTO.data$doublet == T,"HTO_Results"] <- "Doublet"
table(HTO.data$HTO_Results)
#HTO.data$HTO_Results <- factor(HTO.data$HTO_Results)

# doubletFinder
HTO.data$DF_Results <- NA
HTO.data[HTO.data$DFPrediction == "Singlet","DF_Results"] <- "Singlet" #clint
HTO.data[HTO.data$DFPrediction == "Low Confidence" | HTO.data$DFPrediction == "Low Confidence adjusted","DF_Results"] <- "Doublet_low" #clint
HTO.data[HTO.data$DFPrediction == "High Confidence" | HTO.data$DFPrediction == "High Confidence adjusted","DF_Results"] <- "Doublet_high" #clint
table(HTO.data$DF_Results)


### ASSIGN DOUBLETS (HTO + DoubletFinder) HTO_STRICT_GUESS ###
# Hashtags first
HTO.data$HTO_STRICT_GUESS <- HTO.data$max.tags
# assign negatives
HTO.data[HTO.data$negative == T,"HTO_STRICT_GUESS"] <- "Negative"
# assign Doublets
HTO.data[HTO.data$doublet == T,"HTO_STRICT_GUESS"] <- "Doublet"
HTO.data[HTO.data$DF_Results == "Doublet_high","HTO_STRICT_GUESS"] <- "Doublet"
HTO.data[HTO.data$DF_Results == "Doublet_low","HTO_STRICT_GUESS"] <- "Doublet"
table(HTO.data$HTO_STRICT_GUESS)

### ASSIGN DOUBLETS (HTO + DoubletFinder) HTO_LENIENT_GUESS ###
# Hashtags first
HTO.data$HTO_LENIENT_GUESS <- HTO.data$max.tags
# assign negatives
HTO.data[HTO.data$negative == T,"HTO_LENIENT_GUESS"] <- "Negative"
# assign Doublets
HTO.data[HTO.data$doublet == T,"HTO_LENIENT_GUESS"] <- "Doublet"
HTO.data[HTO.data$DF_Results == "Doublet_high","HTO_LENIENT_GUESS"] <- "Doublet"
#HTO.data[HTO.data$doublet.class == "Doublet_low","HTO_LENIENT_GUESS"] <- "Doublet"
table(HTO.data$HTO_LENIENT_GUESS)

#HTO.data$DF_Results <- factor(HTO.data$DF_Results)
############################

## ADD TO SEURATOBJ
# fix stupid error
seuratObj@meta.data$HTOClass <- NULL # BUG FIX
seuratObj@meta.data$HTO_Results <- NULL 
seuratObj@meta.data$DF_Results <- NULL 
# seuratObj@meta.data$FM_Results <- NULL 
seuratObj@meta.data$HTO_STRICT_GUESS <- NULL 
seuratObj@meta.data$HTO_LENIENT_GUESS <- NULL 
# add to seurat metadata 
metadata <- seuratObj@meta.data
HTOClass <- HTO.data[,c("barcodes","HTO_Results","DF_Results","HTO_STRICT_GUESS","HTO_LENIENT_GUESS")]#"FM_Results",
metadata <- merge(metadata,HTOClass,by.x = "barcodes",by.y = "barcodes")

## Make correct order in metadata!!
rownames(metadata)<-metadata$barcodes
all(rownames(metadata)==rownames(seuratObj@meta.data))
metadata<-metadata[seuratObj@meta.data$barcodes,]
all(rownames(metadata)==rownames(seuratObj@meta.data))

seuratObj <- AddMetaData(seuratObj,metadata$HTO_Results,col.name = "HTO_Results")
seuratObj@meta.data$HTO_Results <- factor(seuratObj@meta.data$HTO_Results)

seuratObj <- AddMetaData(seuratObj,metadata$DF_Results,col.name = "DF_Results")
seuratObj@meta.data$DF_Results <- factor(seuratObj@meta.data$DF_Results)

# seuratObj <- AddMetaData(seuratObj,metadata$FM_Results,col.name = "FM_Results")
# seuratObj@meta.data$FM_Results <- factor(seuratObj@meta.data$FM_Results)

seuratObj <- AddMetaData(seuratObj,metadata$HTO_STRICT_GUESS,col.name = "HTO_STRICT_GUESS")
seuratObj@meta.data$HTO_STRICT_GUESS <- factor(seuratObj@meta.data$HTO_STRICT_GUESS)

seuratObj <- AddMetaData(seuratObj,metadata$HTO_LENIENT_GUESS,col.name = "HTO_LENIENT_GUESS")
seuratObj@meta.data$HTO_LENIENT_GUESS <- factor(seuratObj@meta.data$HTO_LENIENT_GUESS)

## Vis extra
LENIENT_GUESS<-seuratObj@meta.data$HTO_LENIENT_GUESS
LENIENT_GUESS_df <- as.data.frame(LENIENT_GUESS) %>%
  group_by(LENIENT_GUESS) %>%  dplyr::count() %>% dplyr::mutate(perc = round(100*n/ncells,2))
LENIENT_GUESS_results <- ggplot(LENIENT_GUESS_df, aes(x = LENIENT_GUESS, y = perc)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = paste("",perc,"%\nn=",n,"")), size=3.5, vjust = -0.3) +
  ggtitle("Classification according to pipeline Maarten") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "", y = "Percentage of cells") +
  ylim(0, 125) +
  theme(axis.text.x = element_text(angle = 45, size=12, hjust = 1))

pdf(file = paste0(output.dir,"Plots/HTO/10_HTO_Lenient_guess_pipeline_Maarten_",experiment,".pdf"), width = 6, height = 5)
LENIENT_GUESS_results
dev.off()

seuratObj$MULTI_ID_merge<-paste0(seuratObj$orig.ident,"_",seuratObj$MULTI_ID)
seuratObj$LENIENT_GUESS_merge<-paste0(seuratObj$orig.ident,"_",seuratObj$HTO_LENIENT_GUESS)

pdf(file = paste0(output.dir,"Plots/HTO/Overview_",experiment,".pdf"), width = 10, height = 12)
DimPlot(seuratObj,group.by = "MULTI_ID_merge", label = F, pt.size = 0.1) + ggtitle("MULTIseqDemux")
DimPlot(seuratObj,split.by = "MULTI_ID_merge", group.by = "MULTI_ID_merge", label = F, pt.size = 0.1, ncol = 4) + ggtitle("MULTIseqDemux")
DimPlot(seuratObj,group.by = "LENIENT_GUESS_merge", label = F, pt.size = 0.1) + ggtitle("LENIENT_GUESS")
DimPlot(seuratObj,split.by = "LENIENT_GUESS_merge", group.by = "LENIENT_GUESS_merge", label = F, pt.size = 0.1, ncol = 4) + ggtitle("LENIENT_GUESS")
# DimPlot(seuratObj,group.by = "HTO_maxID", label = F, pt.size = 0.1) + ggtitle("MAX HTO count")
# DimPlot(seuratObj,split.by = "HTO_maxID", group.by = "HTO_maxID", label = F, pt.size = 0.1, ncol = 2) + ggtitle("MAX HTO count")
dev.off()

#######################################################################################################


