---
title: "Post-precossing"
output: html_document
---

#Post-Processing

After Basic filtering of data we want to take a closer look at each cluster that and see where further processing is necessary 



MOVED CHUNCK FORM PRE-processing

## Manual Cluster slection Seurat Manier
```{r}

selected <- CellSelector(DimPlot(seuratObj))
#selected2 <- CellSelector(DimPlot(seuratObj), ident = 8) 

```




## Manual Cluster selection (Selection of Whole Cluster) (Is dit nog Nodig?)

Functions
```{r}
colorSomeCells<-function(clusterMatrix, coordsTable, cellsToColor){
  clusterMatrix$toColor=FALSE
  clusterMatrix[cellsToColor,which(colnames(clusterMatrix)=="toColor")]<-TRUE
  
  p1 <- ggplot()+
    geom_point(aes_string(x=colnames(coordsTable)[1],y=colnames(coordsTable)[2], colour=clusterMatrix$toColor), data=coordsTable, size=1) +
    scale_color_manual(values=c('TRUE'="orangered",'FALSE'="lightgray")) +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.text=element_text(size=12))
  
  return(p1)
}



```

Selection
```{r}
ClusterData <- seuratObj@meta.data
UMAPTable <-as.data.frame(seuratObj[['RNA_umap']]@cell.embeddings, stringsAsFactors = F)

#Color Cluster Number?
ColorIdent <- 1

wantedCells<-WhichCells(seuratObj, idents = ColorIdent)
colorSomeCells(ClusterData, UMAPTable, wantedCells)

```


```{r}
#Make number for new cluster
totalNrClusters <- max(as.numeric(as.character(Idents(seuratObj))))
NewNrClusters <- totalNrClusters + 1


# Put orignal cluster assigments of cells
seuratObj$seurat_selected_clusters <- as.character(seuratObj$seurat_clusters)

seuratObj$seurat_selected_clusters[selected] <- as.character(NewNrClusters)

######################### Werkt ma cluste naam is NA ##############################
# Replace the old Cluster number of the seleced cell with the new one
#new_levels <- c(levels(seuratObj$seurat_clusters), as.character(NewNrClusters))

#seuratObj$seurat_selected_clusters <- factor(seuratObj$seurat_selected_clusters, levels = new_levels)
########################################################################################

# 2DE CLUSTER VERWIJDERT DE EERST LET OP!!!!!!!!!!!!!!!!!!!!!!!

seuratObj$seurat_selected_clusters <- factor(seuratObj$seurat_selected_clusters)

#Activate the new selected clusters
Idents(seuratObj) <- seuratObj$seurat_selected_clusters


DimPlot(seuratObj, reduction = "RNA_umap", label = T, repel = T, label.size = 4)


```

## Removing Selecetd cluster cluster of choice

```{r}
# Remove Selected
seuratObj <- subset(seuratObj, cells = selected, invert=TRUE)

#Remove specific cluster (Change idents to choose which cluster to remove)
# ClusterCellsRemove <- WhichCells(seuratObj, idents = 3)
# seuratObj <- subset(seuratObj, cells = ClusterCellsRemove, invert=TRUE)



DimPlot(seuratObj, reduction = "RNA_umap", label = T, repel = T, label.size = 4)





# Saving RDS object


