---
title: "Post-precossing"
output: html_document
---



#Post-Processing

After Basic filtering of data we want to take a closer look at each cluster that and see where further processing is necessary 


## Loading the Seurat Object
```{r}
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM3")
FileName <- basename(getwd())

# For SAM2 and SAM3
seuratObj <- readRDS(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Pre-process/SeuratObj_Pre-Process_",FileName))

# For the rest of the datasets
#seuratObj <- readRDS(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/Post-process/",FileName,"/SeuratObj_HTO_",FileName,".rds"))


```


##Making Subsets of the data
```{r}

# Subset: Removing the Negative and Doublets
# Only HTO.data doublets removed ---> scdblfinder doublets are still in the the seuratObj 
ncol(seuratObj)
seuratObjR <- subset(seuratObj,seuratObj@meta.data$HTO_GUESS != "Doublet" & seuratObj@meta.data$HTO_GUESS != "Negative")
ncol(seuratObjR)

PlotSeurat <- DimPlot(seuratObj)+ggtitle(paste0("Graph ",FileName," Clusters"))
PlotSeuratR <- DimPlot(seuratObjR)+ggtitle(paste0("Graph",FileName,""))

PlotSeurat
PlotSeuratR 

```



## Manual Cluster slection Seurat Manier
```{r}

selected <- CellSelector(DimPlot(seuratObjR))

```




## Manual Cluster selection (Selection of Whole Cluster) (Is dit nog Nodig?)

Functions
```{r}
colorSomeCells<-function(clusterMatrix, coordsTable, cellsToColor){
  clusterMatrix$toColor=FALSE
  clusterMatrix[cellsToColor,which(colnames(clusterMatrix)=="toColor")]<-TRUE
  
  p1 <- ggplot()+
    geom_point(aes_string(x=colnames(coordsTable)[1],y=colnames(coordsTable)[2], colour=clusterMatrix$toColor), data=coordsTable, size=1) +
    scale_color_manual(values=c('TRUE'="orangered",'FALSE'="lightgray")) +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.text=element_text(size=12))
  
  return(p1)
}



```

Selection
```{r}
ClusterData <- seuratObj@meta.data
UMAPTable <-as.data.frame(seuratObj[['RNA_umap']]@cell.embeddings, stringsAsFactors = F)

#Color Cluster Number?
ColorIdent <- 1

wantedCells<-WhichCells(seuratObj, idents = ColorIdent)
colorSomeCells(ClusterData, UMAPTable, wantedCells)

```



## Adding A cluster
```{r}
#Make number for new cluster
totalNrClusters <- max(as.numeric(as.character(Idents(seuratObj))))
NewNrClusters <- totalNrClusters + 1
# Put orignal cluster assigments of cells
seuratObj$seurat_selected_clusters <- as.character(seuratObj$seurat_clusters)
seuratObj$seurat_selected_clusters[selected] <- as.character(NewNrClusters)
# 2DE CLUSTER VERWIJDERT DE EERST LET OP!!!!!!!!!!!!!!!!!!!!!!!
seuratObj$seurat_selected_clusters <- factor(seuratObj$seurat_selected_clusters)
#Activate the new selected clusters
Idents(seuratObj) <- seuratObj$seurat_selected_clusters
DimPlot(seuratObj, reduction = "RNA_umap", label = T, repel = T, label.size = 4)


```

## Removing Selecetd cluster or cluster of choice

```{r}
# Remove Selected
seuratObjR <- subset(seuratObjR, cells = selected, invert=TRUE)

#Remove specific cluster (Change idents to choose which cluster to remove)
# ClusterCellsRemove <- WhichCells(seuratObj, idents = 3)
# seuratObj <- subset(seuratObj, cells = ClusterCellsRemove, invert=TRUE)

DimPlot(seuratObjR, reduction = "RNA_umap", label = T, repel = T, label.size = 4)

```


#Annontation Post-Processing of seuratObjR
```{r}
 PostAnnotClust <- DimPlot(seuratObj, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells Before"))

 PostAnnotClustR <- DimPlot(seuratObjR, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells After"))
 
 PostAnnotClust
 PostAnnotClustR

```


# CDC1: Repeat the process for CDC1
```{r}
#Subset: Only CDC 1

ncol(seuratObjR)
# Previous mistake in annotation excel ---> need the whitspace for CDC1
seuratObjCDC1 <- subset(seuratObjR, seuratObjR$sctype_classification == " Dendritic cells 1"| seuratObjR$sctype_classification == "RBC"| seuratObjR$sctype_classification == "Unknown")
ncol(seuratObjCDC1)

#active idents 
Idents(seuratObjCDC1) <- "sctype_classification"

PlotSeuratCDC1 <- DimPlot(seuratObjCDC1,)+ggtitle(paste0("Graph: ",FileName," Annotation All cells After"))
PlotSeuratCDC1

```

## Manual Cluster slection Seurat Manier
```{r}

selected <- CellSelector(DimPlot(seuratObjCDC1))

```
##Remove CDC1 cells
```{r}
seuratObjCDC1 <- subset(seuratObjCDC1, cells = selected, invert=TRUE)

```

## Checking Unknow cells
```{r}

# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjCDC1, expression = sctype_classification == "Unknown")
 
# Making a plot showcasing these genes
PlotUnknown <- FeaturePlot(subset(seuratObjCDC1, cells = unknown_cells),features = c("Cd81","Gcsam","Xcr1","Irf8"))+ggtitle(paste0("Zooming on Unknown cluster: CDC1 Biomarkers"))

PlotUnknown

```

## Reasgin cells
```{r}

seuratObjCDC1$sctype_classification[unknown_cells] <- " Dendritic cells 1"

```

#Annontation Post-Processing of CDC1
```{r}

 PostAnnotClustCDC1 <- DimPlot(seuratObjCDC1, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')
 PostAnnotClustCDC1

```
 
 
```{r}
#Saving Object
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))

saveRDS(seuratObjR,paste0("SeuratObj_Post-Process_",FileName,".rds"))
saveRDS(seuratObjCDC1,paste0("SeuratObj_Post-Process_CDC1_",FileName,".rds"))

pdf(paste0("Graphs Post-Process_",FileName,".pdf"))
PlotSeurat
#PlotSeuratR 
PostAnnotClust
PostAnnotClustR
if (exists("PlotUnknown")) {print(PlotUnknown)}
PlotSeuratCDC1
PostAnnotClustCDC1
dev.off()


```


