---
title: "Post-precossing"
output: html_document
---



#Post-Processing

After Basic filtering of data we want to take a closer look at each cluster that and see where further processing is necessary 


## Loading the Seurat Object
```{r}
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM3")
FileName <- basename(getwd())

# For SAM2 and SAM3
seuratObjP <- readRDS(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/SeuratObj_Pre-Process_",FileName))

```

MOVED CHUNCK FORM PRE-processing

## Manual Cluster slection Seurat Manier
```{r}

selected <- CellSelector(DimPlot(seuratObjP))
#selected2 <- CellSelector(DimPlot(seuratObjP), ident = 8) 

```




## Manual Cluster selection (Selection of Whole Cluster) (Is dit nog Nodig?)

Functions
```{r}
colorSomeCells<-function(clusterMatrix, coordsTable, cellsToColor){
  clusterMatrix$toColor=FALSE
  clusterMatrix[cellsToColor,which(colnames(clusterMatrix)=="toColor")]<-TRUE
  
  p1 <- ggplot()+
    geom_point(aes_string(x=colnames(coordsTable)[1],y=colnames(coordsTable)[2], colour=clusterMatrix$toColor), data=coordsTable, size=1) +
    scale_color_manual(values=c('TRUE'="orangered",'FALSE'="lightgray")) +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.text=element_text(size=12))
  
  return(p1)
}



```

Selection
```{r}
ClusterData <- seuratObjP@meta.data
UMAPTable <-as.data.frame(seuratObjP[['RNA_umap']]@cell.embeddings, stringsAsFactors = F)

#Color Cluster Number?
ColorIdent <- 1

wantedCells<-WhichCells(seuratObjP, idents = ColorIdent)
colorSomeCells(ClusterData, UMAPTable, wantedCells)

```



## Adding A cluster
```{r}
#Make number for new cluster
totalNrClusters <- max(as.numeric(as.character(Idents(seuratObjP))))
NewNrClusters <- totalNrClusters + 1


# Put orignal cluster assigments of cells
seuratObjP$seurat_selected_clusters <- as.character(seuratObjP$seurat_clusters)

seuratObjP$seurat_selected_clusters[selected] <- as.character(NewNrClusters)


# 2DE CLUSTER VERWIJDERT DE EERST LET OP!!!!!!!!!!!!!!!!!!!!!!!

seuratObjP$seurat_selected_clusters <- factor(seuratObjP$seurat_selected_clusters)

#Activate the new selected clusters
Idents(seuratObjP) <- seuratObjP$seurat_selected_clusters


DimPlot(seuratObjP, reduction = "RNA_umap", label = T, repel = T, label.size = 4)


```

## Removing Selecetd cluster or cluster of choice

```{r}
# Remove Selected
seuratObjP <- subset(seuratObjP, cells = selected, invert=TRUE)
#Remove specific cluster (Change idents to choose which cluster to remove)
# ClusterCellsRemove <- WhichCells(seuratObj, idents = 3)
# seuratObj <- subset(seuratObj, cells = ClusterCellsRemove, invert=TRUE)

DimPlot(seuratObjP, reduction = "RNA_umap", label = T, repel = T, label.size = 4)

```

#Annontation Post-Processing
```{r}

source("https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/R/sctype_wrapper.R"); 
seuratObjP <- run_sctype(seurat_object = seuratObjP,
                     assay = "RNA",
                     scaled = TRUE,
                     known_tissue_type="Immune system",
                     custom_marker_file="/Users/samue/Desktop/Stage VIB/CDC Annotatie.xlsx",
                     name="sctype_classification")

# MARKERS: General CDC
# MARKERS: CDC1 and 2 , Migetory and Profilatrate

 PostAnnotClust <- DimPlot(seuratObjP, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')    
 PostAnnotClust


```


```{r}
#Saving Object
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName))

saveRDS(seuratObjP,paste0("SeuratObj_Post-Process_",FileName) )

pdf(paste0("Graphs Before and after Post-Process_",FileName))
AnnotClust
PostAnnotClust
dev.off()


```


