---
title: "Post-precossing"
output: html_document
---
##Functions
```{r}
colorSomeCells<-function(clusterMatrix, coordsTable, cellsToColor){
  clusterMatrix$toColor=FALSE
  clusterMatrix[cellsToColor,which(colnames(clusterMatrix)=="toColor")]<-TRUE
  
  p1 <- ggplot()+
    geom_point(aes_string(x=colnames(coordsTable)[1],y=colnames(coordsTable)[2], colour=clusterMatrix$toColor), data=coordsTable, size=1) +
    scale_color_manual(values=c('TRUE'="orangered",'FALSE'="lightgray")) +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.text=element_text(size=12))
  
  return(p1)
}

```



```{r}
## Packages
library("tidyverse")
library("Seurat")
library("SingleCellExperiment")
library("scater")
library("data.table")
library("ggpubr")
library("gridExtra")
library("fitdistrplus") 
library("dplyr")
library("plyr")
library("caret")
library("openxlsx")
library("ggplot2")
library("tibble")
library("scran")
library("limma")
library("ggrepel")
library("intrinsicDimension")
library("tidyr")
library("purrr")
library("ggrepel")
library("clustree")
library("limma")
library("patchwork")
library("future")
library('RColorBrewer')

```


#Post-Processing

After Basic filtering of data we want to take a closer look at each cluster that and see where further processing is necessary 


## Loading the Seurat Object
```{r}
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM016w")
FileName <- basename(getwd())


#Loading Seaurat object
seuratObj <- readRDS(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Hashing/SeuratObj_HTO_",FileName,".rds"))



```


##Making Subsets of the data
```{r}

# Subset: Removing the Negative and Doublets
# Only HTO.data doublets removed ---> scdblfinder doublets are still in the the seuratObj 
ncol(seuratObj)
seuratObjR <- subset(seuratObj,seuratObj@meta.data$HTO_GUESS != "Doublet" & seuratObj@meta.data$HTO_GUESS != "Negative")
ncol(seuratObjR)

Idents(seuratObjR) <- "HTO_GUESS"

PlotSeurat <- DimPlot(seuratObj, label=T, repel=T )+ggtitle(paste0("Graph ",FileName))
PlotSeuratR <- DimPlot(seuratObjR, label=T, repel=T)+ggtitle(paste0("Graph",FileName))

PlotSeurat
PlotSeuratR 

Idents(seuratObjR) <- "seurat_clusters"

PlotSeuratRClust <- DimPlot(seuratObjR, label=T, repel=T )+ggtitle(paste0("Graph ",FileName," Clusters"))
PlotSeuratRClust

# ALL Doublets are removed

```



## Checking Unknow/ Suspicious cells
```{r}
# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjR, expression = sctype_classification == "Unknown")
# Making a plot showcasing these genes

# Checking If its is CDC1
PlotUnknown1 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Cd81","Gcsam","Xcr1","Irf8"))
PlotUnknown1 <- PlotUnknown1 +plot_annotation(title = "Controling if CDC1")

# Checking if its is CDC2
PlotUnknown2 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Sirpa","S100a4","Cd209a"))
PlotUnknown2 <- PlotUnknown2 +plot_annotation(title = "Controling if CDC2")

# Cheching if Migratory CDC1 
PlotUnknown3 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Cd81","Gcsam","Laptm4b","Ncoa7","Ccr7"))
PlotUnknown3 <- PlotUnknown3 +plot_annotation(title = "Controling if Migartory CDC1")

PlotUnknown1
PlotUnknown2
PlotUnknown3

# CDC1 Only Irf8 is show to be present in almost all cells. For CDC2 only S100a4 show clearly at on side of the cluster,but at a realetively low count when having a closer looks, For Migratory cells there is barely any CRR7 expersion showing this cluster is likely migratory cells. Additionaly when looking at the pre-processing graphs, no cell type show clear expression in the Unknown cluster and the ADT count is low in the cluster compared to the rest of Umap. Most likely this these cells are low quality with no clear celltype, 
```


## Manual Cluster selection of Whole cluster

Checking the Doublet count of Cluster 12/ Unknown cell type
Selection
```{r}
ClusterData <- seuratObj@meta.data
UMAPTable <-as.data.frame(seuratObj[['RNA_umap']]@cell.embeddings, stringsAsFactors = F)
#Color Cluster Number?
ColorIdent <- 12
wantedCells<-WhichCells(seuratObjR, idents = ColorIdent)
PrecentageDoublet <- (length(WhichCells(seuratObjR, expression = scDblFinder_class=="doublet", cells = wantedCells))/length(WhichCells(seuratObjR,wantedCells)))*100
PrecentageDoublet <- paste0(round(PrecentageDoublet,2),"%")
PrecentageDoublet
ClustRemoveMap1 <- colorSomeCells(ClusterData, UMAPTable, wantedCells)+ggtitle(paste0("Cluster ",ColorIdent, " = ",PrecentageDoublet," Doublets"))
ClustRemoveMap1

# Has a Almost no doublets
```


## Removing Selecetd cluster or cluster of choice

```{r}
# Remove Selected
# Cluster 12 has a low quality and is thus removed

#Remove specific cluster (Change idents to choose which cluster to remove)
 ClusterCellsRemove <- WhichCells(seuratObjR, idents = 12)
 seuratObjR <- subset(seuratObjR, cells = ClusterCellsRemove, invert=TRUE)

DimPlot(seuratObjR, reduction = "RNA_umap", label = T, repel = T, label.size = 4)

```






#Annontation Post-Processing of seuratObjR
```{r}
 PostAnnotClust <- DimPlot(seuratObj, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells Before"))

 PostAnnotClustR <- DimPlot(seuratObjR, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells After"))
 
 PostAnnotClust
 PostAnnotClustR

```


# CDC1: Repeat the process for CDC1
```{r}
#Subset: Only CDC 1

ncol(seuratObjR)
# Previous mistake in annotation excel ---> need the whitspace for CDC1
seuratObjCDC1 <- subset(seuratObjR, seuratObjR$sctype_classification == " Dendritic cells 1"| seuratObjR$sctype_classification == "Migratory dendritic cells 2" | seuratObjR$sctype_classification == "Proliferating DCs")
ncol(seuratObjCDC1)

#active idents 
Idents(seuratObjCDC1) <- "sctype_classification"

PlotSeuratCDC1 <- DimPlot(seuratObjCDC1,)+ggtitle(paste0("Graph: ",FileName," Annotation CDC1s Before"))
PlotSeuratCDC1

```


## Checking Migratory cells
```{r}

# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjCDC1, expression = sctype_classification == "Migratory dendritic cells 2")
 
# Making a plot showcasing these genes
PlotUnknown <- FeaturePlot(subset(seuratObjCDC1, cells = unknown_cells),features = c("Cd81","Gcsam","Laptm4b","Ncoa7","Ccr7
"))

PlotUnknown <- PlotUnknown +plot_annotation(title = "Zooming on Unknown cluster: CDC1 Biomarkers")

PlotUnknown

#The lower section are Migratory CDC1, which we want to isolate. 

```

## Reasgin cells
```{r}
selected <- CellSelector(DimPlot(seuratObjCDC1))
seuratObjCDC1$sctype_classification[selected] <- "Migratory dendritic cells 1"

```
#Cleaning Up far off cells and removing Migratory CDC2
```{r}
selected <- CellSelector(DimPlot(seuratObjCDC1))
```

```{r}
seuratObjCDC1 <- subset(seuratObjCDC1, cells = selected, invert=TRUE)

```


##Annontation Post-Processing of CDC1
```{r}

 PostAnnotClustCDC1 <- DimPlot(seuratObjCDC1, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle("CDC Final result")
 PostAnnotClustCDC1

```
 
# Notes
```{r}

blurb = paste("\n   Notes for The Post-Processing of SAM2.\n",
         "
		- Almost All Doublets removed when removing HTO.Data

    - Unknown Cells ---> Low quality ---> Removed
		
		- Check Migratory CDC2 Cluster 11
			- Lower part: Migratory CDC1
			- Upper Part: Migratory CDC2")
Notes <- ggplot() + 
  annotate("text", x = 4, y = 25, size=4, label = blurb) + 
  theme_void()
Notes

```

#Saving Object
```{r}
#Saving Object
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))

saveRDS(seuratObjR,paste0("SeuratObj_Post-Process_",FileName,".rds"))
saveRDS(seuratObjCDC1,paste0("SeuratObj_Post-Process_CDC1_",FileName,".rds"))

setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))
pdf(paste0("Graphs Post-Process_",FileName,".pdf"), width = 14,
  height = 10)

PlotSeurat 
PlotSeuratR 
PostAnnotClust 
PostAnnotClustR
ClustRemoveMap1
PlotUnknown1
PlotUnknown2
PlotUnknown3
if (exists("PlotUnknown")) {print(PlotUnknown)}
PlotSeuratCDC1
PostAnnotClustCDC1
Notes
dev.off()


```


