---
title: "Pre-processing"
output:
  pdf_document: default
  html_document: default
---


Pre-processing of CITE-seq data This Script is the first and will be used to pre-process SAM2 Provided data

```{r}

###############################################
#LOADING PACKAGE
###############################################

library("renv")
library("tidyverse")
library("Seurat")
library("SingleCellExperiment")
library("scater") 
library("scran") # Note for Windows --> Bluster dependencie doesnt compile properly in windows, mannulay add the bluster package to library. Download ---> https://bioc.r-universe.dev/bluster
library('fields')
library("dplyr")
library("stringr")
library("readr")
library("ggplot2")
library("HGNChelper") #For sc_type nesseacry
library("scDblFinder")
library("readxl")
library("patchwork")
library("presto") 
# issue downloading presto --> use following commands:
#pak::pak("RcppArmadillo@0.12.8.0.0", ask = FALSE)
#.rs.restartR()
#pak::pak("immunogenomics/presto")
library("clustree") # Note:Be sure you have the 4.5 version of Rtools
library("openxlsx")
```

```{r}
#############################################
#RNA
############################################
setwd("/Users/samue/Desktop/Stage VIB/RawData/VBO005")
FileName <- basename(getwd())
rawData <- Read10X("filtered_feature_bc_matrix")
rawDataRNA <- rawData[["Gene Expression"]]
# rawDataRNA <- as.matrix(rawData$Gene Expression) Keeps all Zero values, but makes object to big for current pc

# Rawdata is 6.1 GB, it can be loaded but not examined ---> Took a subset of cells
# rawDataRNA <- rawDataRNA[, 1:2000]

```

```{r}
sce<-SingleCellExperiment(list(counts=rawDataRNA))
# Everything starting with MT put in is.mito vector
is.mito <- grepl("^MT-", rownames(sce), ignore.case = TRUE)

#Scuttle function: addPerCellQC: Add QC metrics to a SummarizedExperiment
#QCmetric: Compute per-cell quality control metrics for a count matrix or a SingleCellExperiment. 

sce<- addPerCellQC(sce, subsets=list(Mito=is.mito))

# Make Metadata dataframe
metaData<-data.frame("staticNr"=colnames(rawDataRNA), 
                     "nGene"=sce$detected,
                     "nUMI"=sce$sum,
                     "percent.mito"=sce$subsets_Mito_percent, 
                     stringsAsFactors = F)
#Rownames fixen
rownames(metaData)<-metaData$staticNr
metaData$staticNr<-1


```

```{r}
# FILTERING Test

sampleName<-"GSM_2677817"
experiment <- sampleName
batch <- rep(sampleName, colnames(rawDataRNA) %>% length())

# Setting cut offs (Increased the cutoffs, Still Increase?)
# Nummber of genes
nmad_low_feature<-3
nmad_high_feature<-3

# Total counts all gene in a cell
nmad_low_UMI<-3
nmad_high_UMI<-3

# Precentage Mitchondrial gene
nmad_high_mito<- 5

#Filter both Low and High outliers out
feature.drop.low <- isOutlier(sce$detected, nmads=nmad_low_feature, type="lower", log=TRUE,batch = batch)
feature.drop.high <- isOutlier(sce$detected, nmads=nmad_high_feature, type="higher", log=TRUE,batch = batch)
# Putting everything togheter
feature.drop<-as.logical(feature.drop.low + feature.drop.high,batch = batch)

#Filter both Low and High outliers out
libsize.drop.low <- isOutlier(sce$sum, nmads=nmad_low_UMI, type="lower", log=TRUE,batch = batch)
libsize.drop.high <- isOutlier(sce$sum, nmads=nmad_high_UMI, type="higher", log=TRUE,batch = batch)

# Putting everything togheter
libsize.drop<-as.logical(libsize.drop.low+libsize.drop.high)

#Filtering High out
mito.drop.high <- isOutlier(sce$subsets_Mito_percent, nmads=nmad_high_mito, type="higher",batch = batch)
mito.drop <- as.logical(mito.drop.high)


# Add dropped cells to metadata
metaData$nGene.drop=feature.drop
metaData$nUMI.drop=libsize.drop
metaData$mito.drop=mito.drop
metaData$final.drop=feature.drop | libsize.drop | mito.drop

#Removing the outliers
#The filted data is put in a seprate object
scef <- sce[,!(libsize.drop | feature.drop | mito.drop)]

# Creating a Filter Metadata for the plots
metaDataF<-data.frame("staticNr"=colnames(scef),
                     "nGene"=scef$detected,
                     "nUMI"=scef$sum,
                     "percent.mito"=scef$subsets_Mito_percent, 
                     stringsAsFactors = F)
rownames(metaDataF)<-metaDataF$staticNr
metaDataF$staticNr<-1

# Defining the cutoffs
ul.mito <- attr(mito.drop.high,'thresholds')[2]
ll.cd <- attr(libsize.drop.low,'thresholds')[1]
ul.cd <- attr(libsize.drop.high,'thresholds')[2]
ll.ng <- attr(feature.drop.low,'thresholds')[1]
ul.ng <- attr(feature.drop.high,'thresholds')[2]
```

#Graphs Before and after

Graph of data Before and After Filtering Here we make a scatter, histogram and violin plot of the data before and after its gets filtered (Note: Verbeter look van grafieken)

```{r}

MitoPrecentage <- sce$subsets_Mito_percent

sctplt1 <- ggplot(metaData,aes(x=nUMI, y=nGene)) + 
  geom_point(aes(colour = MitoPrecentage ))+
  scale_colour_gradientn(colours=terrain.colors(10), limits=c(0,4))+
  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.5)+
geom_hline(yintercept = ll.ng,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_hline(yintercept = ul.ng,linetype="dotted", 
                color = "red", size=1.5)+
    theme_bw()

MitoPrecentageF <- scef$subsets_Mito_percent

sctplt2 <- ggplot(metaDataF,aes(x=nUMI, y=nGene)) + 
  geom_point(aes(colour = MitoPrecentageF ))+
  scale_colour_gradientn(colours=terrain.colors(10))+
  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.5)+
geom_hline(yintercept = ll.ng,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_hline(yintercept = ul.ng,linetype="dotted", 
                color = "red", size=1.5)+
  theme_bw()

sctplt1 
sctplt2

# Zoomed in Plots
sctplt1+ coord_cartesian(ylim = c(0, 2500),xlim = c(0,2500))
sctplt2+ coord_cartesian(ylim = c(0, 2500),xlim = c(0,2500))

```

```{r}
hist1 <- ggplot(metaData, aes(x = nUMI)) +
  geom_histogram(binwidth=100)+  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.1)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.1)+
  theme_bw()

hist2 <- ggplot(metaDataF, aes(x = nUMI)) +
  geom_histogram(binwidth=100)+
    geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.1)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.1)+
  theme_bw()+

hist1 
hist2

```

```{r}

vlplt1 <- ggplot(metaData,aes(x=nUMI, y=nGene)) + 
  geom_violin(fill="red")+
  theme_bw()

vlplt2 <-ggplot(metaDataF,aes(x=nUMI, y=nGene)) + 
  geom_violin(fill= "green")+
  theme_bw()

vlplt1 + vlplt2
```

## Mitochondrial gene Percentage plot

```{r}
Mito1 <- ggplot(metaData, aes(x=MitoPrecentage)) + 
  geom_histogram(binwidth = 0.1)+
  geom_vline(xintercept = ul.mito,linetype="dotted", 
                color = "blue", size=1.5)

Mito2 <- ggplot(metaDataF, aes(x=MitoPrecentageF)) + 
  geom_histogram(binwidth = 0.1)+
  geom_vline(xintercept = ul.mito,linetype="dotted", 
                color = "blue", size=1.5)

Mito1
Mito2

# Zoom in grafiek 1
Mito1 + coord_cartesian(xlim = c(0,10))




```

##How many cells were removed during filtering?

```{r}
BeforeFiltering <- ncol(sce)
AfterFilering <- ncol(scef)
#AfterscDbl <-  table(scef$scDblFinder.class)

print("How many cells removed?")
print(paste("Before Filtering",BeforeFiltering))
print(paste("After Filtering",AfterFilering))
#print(paste("After scDblFinder:"))
#AfterscDbl



```

##Creating Seurat Object

```{r}
rawDataFiltered<-rawDataRNA[rownames(scef),colnames(scef)]
# Creating ADT RawData
rawDataADT <- as.matrix(rawData$`Antibody Capture`)
rawDataADT <- rawDataADT

rm(rawData)
rm(rawDataRNA)
rm(sce)
gc()

# CREATE SEURAT OBJECT
cells.to.keep <- colnames(scef)
seuratObj <- CreateSeuratObject(rawDataFiltered, project = experiment, min.cells=1)

#Adding scDblFinder data to the Seuratobject
#seuratObj$scDblFinder.score <- scef$scDblFinder.score
#seuratObj$scDblFinder.class <- scef$scDblFinder.class

# Removing Object for performance
rm(rawDataFiltered)
rm(scef)
gc()


```

##Normailzation

```{r}
#Creating Seurat Object
seuratObj <- FindVariableFeatures(seuratObj, selection.method = 'vst', nfeatures = 2000)

 seuratObj <- NormalizeData(seuratObj, normalization.method = "LogNormalize", scale.factor = 1e4)

```

##Dimensional reduction

```{r}

all.genes <- rownames(seuratObj)
seuratObj <- ScaleData(seuratObj, features = all.genes)

#seuratObj <- wilcoxauc(seuratObj, 'cell_type', seurat_assay = 'RNA') # Presto not in CRAN, Recieve error when using recommend command devtools::install_github("immunogenomics/presto")

seuratObj <- RunPCA(seuratObj, 
                    features = VariableFeatures(object = seuratObj), 
                    ndims.print = 1:5, nfeatures.print = 10,
                    assay = "RNA",
                    reduction.name = "RNA_pca",
                    reduction.key = "rnaPC_")
```

## Optimize PCA

```{r}

Elbow <- ElbowPlot(seuratObj, reduction = "RNA_pca", ndims = 40)
Elbow
```

```{r}

print(seuratObj[["RNA_pca"]], dims = 1:5, nfeatures = 5)


```

##Finding Best Dimension Clustering of cells

```{r}
# Test more than 14 dimensions (see example script)
StartingDims <- 10 # Always do Starting Amount of Dims - 1
EndingDims <- 25
TotalDims <- EndingDims - StartingDims

print(paste0("Working on Dims Starting form ",StartingDims, " to Dims ", EndingDims ," Total: ",TotalDims))

ListDims <- seq(1:TotalDims+1)
for(i in ListDims){
  #Creating Mulitple Cluster Maps with Different Dims
  StartingDims <- StartingDims + 1
  seuratObj <- FindNeighbors(seuratObj, dims = 1:StartingDims, reduction = "RNA_pca")
  seuratObj <- FindClusters(seuratObj, resolution = 0.5)
  seuratObj <- RunUMAP(seuratObj, dims = 1:StartingDims,reduction = "RNA_pca", reduction.name = "RNA_umap" )
  
  #Title for UMap
  UMAPTitle <- paste0("UMAP Number = ",StartingDims)
  UMAPgraph  <-DimPlot(seuratObj, reduction = "RNA_umap",label = T, repel = T, label.size = 4)+ggtitle(UMAPTitle)
  print(UMAPgraph)

}

```

## Loop For best Resolution of the found dims

```{r}

LoopRes <- seq(0.5,1.5,0.1) # Always do Starting Amount of Dims - 1

# Fill in the BEST dims found form the pervious chunck(NOTE: 2 dims=1:? to fill in)!
for(i in LoopRes){
  
  #Creating Mulitple Cluster Maps with Different Resolutions
  seuratObj <- FindNeighbors(seuratObj, dims = 1:25, reduction = "RNA_pca")
  seuratObj <- FindClusters(seuratObj, resolution = i)
  seuratObj <- RunUMAP(seuratObj, dims = 1:25,reduction = "RNA_pca", reduction.name = "RNA_umap" )
  
  #Title for UMap
  UMAPTitle <- paste0("Resolution Number = ",i)
  UMAPgraph  <-DimPlot(seuratObj, reduction = "RNA_umap",label = T, repel = T, label.size = 4)+ggtitle(UMAPTitle)
  print(UMAPgraph)
}

#Test Clustree
  Tree <- clustree(seuratObj, prefix = "RNA_snn_res.")
Tree
# Best resolution = 0.9

```

# Best Clustering of cells

```{r}
#Put the best Dims and Resolution here in this graph 
seuratObj <- FindNeighbors(seuratObj, dims = 1:25, reduction = "RNA_pca")
  seuratObj <- FindClusters(seuratObj, resolution = 0.9)
  seuratObj <- RunUMAP(seuratObj, dims = 1:25,reduction = "RNA_pca", reduction.name = "RNA_umap" )
  BestCluster <- DimPlot(seuratObj, reduction = "RNA_umap",label = T, repel = T, label.size = 4)
  BestCluster
```

##Finding Cluster Biomarkers

```{r}
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Pre-process/"))


ClusterRNA <- FindAllMarkers(seuratObj, only.pos = TRUE, test.use="wilcox") #use test.use="wilcox" to use presto
ClusterRNA<-ClusterRNA[order(ClusterRNA$p_val_adj, decreasing = FALSE), ]

ClusterRNA$score<- ClusterRNA$pct.1/(ClusterRNA$pct.2+0.01)*ClusterRNA$avg_log2FC
head(ClusterRNA)

totalNrClusters<-max(as.numeric(names(table(ClusterRNA$cluster))))
totalNrClusters <- totalNrClusters+1
markersList<-list()

for(i in 1:totalNrClusters){
  clusterNr<-i-1
  
  tmp<-ClusterRNA[ClusterRNA$cluster==clusterNr,]
  tmp$score<-tmp$pct.1/(tmp$pct.2+0.01)*tmp$avg_log2FC
  
  markersList[[i]]<-tmp[order(tmp$score, decreasing=TRUE),]
}
totalNrClusters <- totalNrClusters-1
names(markersList)<-paste0("cluster",0:totalNrClusters)

### Write to Excel

write.xlsx(markersList,paste0("SeuratObj_Marker_RNA_",FileName,".xlsx"))
           
saveRDS(ClusterRNA, paste0("SeuratObj_Marker_RNA_",FileName))


```

## Plotting Biomarkers

```{r}

#FeaturePlot(seuratObj, features = c("Ncr1", "Cacnb3", "Pclaf", "Spc24", "Cd3g", "Cdk1"))

```

#ADT

```{r}

raw.names <- rownames(rawDataADT)
cells.use  <- intersect(colnames(rawDataADT), colnames(seuratObj))
ABS.use  <- rownames(rawDataADT)
rawDataADT <- rawDataADT[ABS.use, cells.use]
seuratObj[["ADT"]] <- CreateAssayObject(counts = rawDataADT[,colnames(seuratObj)])

#Normalization
seuratObj <- NormalizeData(seuratObj, assay = "ADT", normalization.method = "CLR", verbose=T)

seuratObj <- FindVariableFeatures(seuratObj,assay="ADT",selection.method = "vst", nfeatures=nrow(rawDataADT))


#Dimensenioanly Reduction
seuratObj <- ScaleData(seuratObj, assay = "ADT")

seuratObj <- RunPCA(seuratObj, 
                    features = VariableFeatures(object = seuratObj, assay = "ADT"), 
                    ndims.print = 1:5, nfeatures.print = 10,
                    assay = "ADT",
                    reduction.name = "ADT_pca",
                    reduction.key = "adtPC_")
# Finding Cluster

StartingDimsADT <- 14 # Always do Starting Amount of Dims - 1
EndingDimsADT <- 25
TotalDimsADT <- EndingDimsADT - StartingDimsADT

print(paste0("Working on Dims Starting form ",StartingDimsADT, " to Dims ", EndingDimsADT ," Total: ",TotalDimsADT))

ListDimsADT <- seq(1:TotalDimsADT+1)

for(i in ListDimsADT){
  #Creating Mulitple Cluster Maps with Different Dims
  StartingDimsADT <- StartingDimsADT + 1
  seuratObj <- FindNeighbors(seuratObj, dims = 1:StartingDimsADT, reduction = "ADT_pca")
  seuratObj <- FindClusters(seuratObj, resolution = 0.5)
  seuratObj <- RunUMAP(seuratObj, dims = 1:StartingDimsADT,reduction = "ADT_pca", reduction.name = "ADT_umap" )
  
  #Title for UMap
  UMAPTitleADT <- paste0("UMAP Number = ",StartingDimsADT)
  UMAPgraphADT  <-DimPlot(seuratObj, reduction = "ADT_umap",label = T, repel = T, label.size = 4)+ggtitle(UMAPTitleADT)
  print(UMAPgraphADT)
}


#LoopRes <- seq(0.5,1.5,0.1) # Always do Starting Amount of Dims - 1

# Fill in the BEST dims found form the pervious chunck(NOTE: 2 dims=1:? to fill in)!
for(i in LoopRes){
  
#Creating Mulitple Cluster Maps with Different Resolutions
  seuratObj <- FindNeighbors(seuratObj, dims = 1:25, reduction = "ADT_pca")
  seuratObj <- FindClusters(seuratObj, resolution = i)
  seuratObj <- RunUMAP(seuratObj, dims = 1:25,reduction = "ADT_pca", reduction.name = "ADT_umap" )
  
  #Title for UMap
  UMAPTitle <- paste0("Resolution Number ADT = ",i)
  UMAPgraph  <-DimPlot(seuratObj, reduction = "ADT_umap",label = T, repel = T, label.size = 4)+ggtitle(UMAPTitle)
 print(UMAPgraph)
}

#Test Clustree
#TreeADT <- clustree(seuratObj, prefix = "ADT_snn_res.")
#TreeADT

#Best Cluster (Change dims)
seuratObj <- FindNeighbors(seuratObj, reduction = "ADT_pca",dims = 1:25)
seuratObj <- FindClusters(seuratObj, resolution = 0.5)


# UMAP
seuratObj <- RunUMAP(seuratObj, dims = 1:25, assay = "ADT", reduction = "ADT_pca", reduction.name ="ADT_umap" )
DimPlot(seuratObj, reduction = "ADT_umap", label = T, repel = T, label.size = 4)

#Finding Markers
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Pre-process/"))

ClusterADT6 <- FindAllMarkers(seuratObj, only.pos = TRUE, assay = "ADT")
head(ClusterADT6, n = 6)

saveRDS(ClusterADT6, paste0("SeuratObj_Marker_ADT_",FileName))

write.xlsx(ClusterADT6,paste0("SeuratObj_Marker_ADT_",FileName,".xlsx"))


FeaturePlot(seuratObj, features = c("CD24", "CD9", "CD371	", "CD272", "XCR1", "CD29"))

```

#Annotation Cells

```{r}

## readRDS of your sample before
# sample <- readRDS("/absolute/path/sample.RDS");
source("https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/R/sctype_wrapper.R"); 
seuratObj <- run_sctype(seurat_object = seuratObj,
                     assay = "RNA",
                     scaled = TRUE,
                     known_tissue_type="Immune system",
                     # Used Custom Annotation
                     custom_marker_file="/Users/samue/Desktop/Stage VIB/CDC Annotatie.xlsx",
                     name="sctype_classification")

# MARKERS: General CDC
# MARKERS: CDC1 and 2 , Migetory and Profilatrate

 AnnotClust <- DimPlot(seuratObj, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')    
 AnnotClust
```

# After Clustering Filitering (see notes and scripts (general))

```{r}
# Top Markers per Cluster
totalNrClusters<-max(as.numeric(names(table(ClusterRNA$cluster))))
BioMarkerList <- list()

for(i in 1:totalNrClusters){
  tmp <- ClusterRNA[ClusterRNA$cluster==i,]
  # Scoring
  # pct 1 percentage cell in the cluster that express that gene
  # pct 2 percentage cell in other clusters that express that gene
  # avg_log2FC is a weight to add to score
  tmp$score<-tmp$pct.1/(tmp$pct.2+0.001)*tmp$avg_log2FC
  BioMarkerList[[i]]<-tmp[order(tmp$score, decreasing=TRUE),] #Already sorted by score
  TopMarkersperCluster <- list(head(BioMarkerList[[i]]$gene))
  print(paste("Top Markers of Cluster:",i,"=", TopMarkersperCluster))
}

#tmp$score<-tmp$pct.1/(tmp$pct.2+0.01)*tmp$avg_log2FC?? Score voor biomarkers
# Sort by Frequencie?

```

## Finding Doublets

```{r}
# Make Seuratobject a SingleCellExpirment Object
Doublets <- as.SingleCellExperiment(seuratObj)
Doublets$seurat_cluster <- seuratObj$seurat_clusters

# Find the Doublets
Doublets <- scDblFinder(Doublets, clusters="seurat_cluster") 

#Doublets per Cluster
#dbl <- findDoubletClusters(counts(Doublets), Doublets$seurat_cluster)

# Work within Seuratobject to compare cluster to scDblFinder.class

# Add to the Orginal SeuratObject
seuratObj$scDblFinder_class <- Doublets$scDblFinder.class
seuratObj$scDblFinder_score <- Doublets$scDblFinder.score


 DoubletsMap <- FeaturePlot(object = seuratObj, features = "scDblFinder_score" , cols = c("grey", "blue"),reduction = "RNA_umap", min.cutoff = 'q2', max.cutoff = 'q98', pt.size = 0.7)
DoubletsMap


cellsNames <- droplevels(seuratObj$seurat_clusters)
TrueDoubles <- seuratObj$scDblFinder_class


ClusterDoublets <- as.data.frame(
  table(cellsNames[TrueDoubles == "doublet"])
)
# ADD percentage !!!
AfterscDbl <-table(seuratObj$scDblFinder_class)
print(paste("After scDblFinder:"))
AfterscDbl
ClusterDoublets
# Remove Created object
rm(Doublets)
gc()

```

## Control if Mitochondrian gene Precentage for each gene

```{r}
seuratObj[["percent.mt"]] <- PercentageFeatureSet(seuratObj, pattern = "^mt-")

MitoMap <- FeaturePlot(object = seuratObj, features = "percent.mt" , cols = c("grey", "blue"),reduction = "RNA_umap", min.cutoff = 'q2', max.cutoff = 'q98', pt.size = 0.7)
MitoMap

# Goei Cutoffs for Mito gene Precentage --> 10%?
# Show on the plot (Aantonen als mit gene geconcentreed zijn)
```

##Cluster ADT count

```{r}

 ADTMap <- FeaturePlot(object = seuratObj, features = "nFeature_ADT" , cols = c("grey", "blue"),reduction = "RNA_umap", min.cutoff = 'q2', max.cutoff = 'q98', pt.size = 0.7)
ADTMap

# nCount total ADT per cell
# nfeature how many different ADT per cell 
# Use nfeatuere ADT to calculate average ADT per cluster
# nfeaute let op probleem dat lage cell kwaliteit een hoge count hebben door veel makkelijke bindingen

# FeaturePlot(object = seuratObj, features = ExcelMarker, cols = c("grey", "blue"), 
#Gebruik nfeauter metafa data in the featureplot to make graph



# Good Cutoffs also 10%?
# Ploten on RNA_UMAP and ADT_UMAP
```

# Add Manual Clustering (Remove the markers out of excel and shown manually) (Automatisch uit excel halen)

```{r}
AnnotData <- read_xlsx(path = "/Users/samue/Desktop/Stage VIB/CDC Annotatie.xlsx")
AnnotData

plot_list_FL <- list()
plot_list_TR <- list()

for (i in 1:nrow(AnnotData)){
  ExcelMarker <- unlist(strsplit(AnnotData$geneSymbolmore1[row.names(AnnotData)==i],","))
  #Have To split it up because FeaturePlot see list of genes as 1 name
  AnnotTitle <- paste0(AnnotData$cellName[row.names(AnnotData)==i],"  False ORDER")
  
  # Featureplot best used for looking per gene
  print(AnnotTitle)
  p <- FeaturePlot(object = seuratObj, features = ExcelMarker, cols = c("grey", "blue"), 
            reduction = "RNA_umap", min.cutoff = 'q2', max.cutoff = 'q98', pt.size = 0.7,order = FALSE)
  p_combined <- p + plot_annotation(title = AnnotTitle)
  
  plot_list_FL[[i]] <- p_combined
  
  print(plot_list_FL[[i]])
   
}

for (i in 1:nrow(AnnotData)){
  ExcelMarker <- unlist(strsplit(AnnotData$geneSymbolmore1[row.names(AnnotData)==i],","))
  #Have To split it up because FeaturePlot see list of genes as 1 name
  AnnotTitle <- paste0(AnnotData$cellName[row.names(AnnotData)==i],"  True Order")
  
  # Featureplot best used for looking per gene
  print(AnnotTitle)
  p <- FeaturePlot(object = seuratObj, features = ExcelMarker, cols = c("grey", "blue"), 
            reduction = "RNA_umap", min.cutoff = 'q2', max.cutoff = 'q98', pt.size = 0.7,order = TRUE)
  p_combined <- p + plot_annotation(title = AnnotTitle)
  plot_list_TR[[i]] <- p_combined
  print(plot_list_TR[[i]])
   
  }

ExcelMarker
# Look for Seurat Function Module to bring all gene togheter in 1 plot

```

# Markdown note for Datasets

SAM2:

Resolution is kept at 0.7, 0.7 and 0.8 quite similar but starting form 0.9 the amount of clusters increase dramatically. Doublets graph: There are 3 obvious concentration of doublets that have to be removed (left structure, in the valley of the biggest structure and on the border of the top structure. This has to be further confirmed by determining the cell type Mito: No obvious problems ADT: No obvious problems

## Saving R object

```{r}
#Set folder
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Pre-process/"))

# Save Object with everything Before Post-Processing
saveRDS(seuratObj,paste0("SeuratObj_Pre-Process_",FileName) )
# Saving Graphs
pdf(paste0("Graphs_Pre-Process_",FileName), width = 14,
  height = 10)
sctplt1 
sctplt2
hist1 
hist2
vlplt1 + vlplt2
Elbow
Tree
#TreeADT
BestCluster
AnnotClust
DoubletsMap
MitoMap
ADTMap
plot_list_FL
plot_list_TR

dev.off()
# Save object with everything after Post- Processing
# Save Object with only (Mig and resident) CDC 1

```
