---
title: "Post-precossing"
output: html_document
---
##Functions
```{r}
colorSomeCells<-function(clusterMatrix, coordsTable, cellsToColor){
  clusterMatrix$toColor=FALSE
  clusterMatrix[cellsToColor,which(colnames(clusterMatrix)=="toColor")]<-TRUE
  
  p1 <- ggplot()+
    geom_point(aes_string(x=colnames(coordsTable)[1],y=colnames(coordsTable)[2], colour=clusterMatrix$toColor), data=coordsTable, size=1) +
    scale_color_manual(values=c('TRUE'="orangered",'FALSE'="lightgray")) +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.text=element_text(size=12))
  
  return(p1)
}

```



```{r}
## Packages
library("tidyverse")
library("Seurat")
library("SingleCellExperiment")
library("scater")
library("data.table")
library("ggpubr")
library("gridExtra")
library("fitdistrplus") 
library("dplyr")
library("plyr")
library("caret")
library("openxlsx")
library("ggplot2")
library("tibble")
library("scran")
library("limma")
library("ggrepel")
library("intrinsicDimension")
library("tidyr")
library("purrr")
library("ggrepel")
library("clustree")
library("limma")
library("patchwork")
library("future")
library('RColorBrewer')

```


#Post-Processing

After Basic filtering of data we want to take a closer look at each cluster that and see where further processing is necessary 


## Loading the Seurat Object
```{r}
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM3")
FileName <- basename(getwd())

# Loading in Seurat object
seuratObj <- readRDS(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Pre-process/SeuratObj_Pre-Process_",FileName))

#Count for barplot
nCellsSeurat <- ncol(seuratObj)


```


##Starting plot
```{r}
PlotSeurat <- DimPlot(seuratObj, label=T, repel=T )+ggtitle(paste0("Graph ",FileName," Clusters"))
PlotSeurat

```



## Manual Cluster selection of part of a cluster
```{r}

selected <- CellSelector(DimPlot(seuratObj))

PrecentageDoublet <- (length(WhichCells(seuratObj, expression = scDblFinder_class=="doublet", cells = selected))/length(WhichCells(seuratObj, selected)))*100
PrecentageDoublet <- paste0(round(PrecentageDoublet,2),"%")

PrecentageDoublet
# Part of Cluster 11 = "92.31%" Doublets

```




## Manual Cluster selection of Whole cluster

Selection
```{r}
ClusterData <- seuratObj@meta.data
UMAPTable <-as.data.frame(seuratObj[['RNA_umap']]@cell.embeddings, stringsAsFactors = F)

#CLuster Number checked: 9,17,11
ColorIdent <- 11

wantedCells<-WhichCells(seuratObj, idents = ColorIdent)

PrecentageDoublet <- (length(WhichCells(seuratObj, expression = scDblFinder_class=="doublet", cells = wantedCells))/length(WhichCells(seuratObj,wantedCells)))*100

PrecentageDoublet <- paste0(round(PrecentageDoublet,2),"%")
PrecentageDoublet

# Change map number for each checked cluster to keep maps separate
ClustRemoveMap3 <- colorSomeCells(ClusterData, UMAPTable, wantedCells)+ggtitle(paste0("Cluster ",ColorIdent, " = ",PrecentageDoublet," Doublets"))


ClustRemoveMap1
ClustRemoveMap2
ClustRemoveMap3
```


## Removing Selecetd cluster or cluster of choice

```{r}
# Remove Selected # part of Cluster 11 removed
seuratObj <- subset(seuratObj, cells = selected, invert=TRUE)

#Remove specific cluster (Removed cluster 9 and 17)
 ClusterCellsRemove <- WhichCells(seuratObj, idents = c(9,17))
 seuratObj <- subset(seuratObj, cells = ClusterCellsRemove, invert=TRUE)

DimPlot(seuratObj, reduction = "RNA_umap", label = T, repel = T, label.size = 4)

```



#Annontation Post-Processing of seuratObj
```{r}
 PostAnnotClust <- DimPlot(seuratObj, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells Before"))

 PostAnnotClust

```


# CDC1: Repeat the process for CDC1
```{r}
#Subset: Only CDC 1

ncol(seuratObj)
# Previous mistake in annotation excel ---> need the whitspace for CDC1
seuratObjCDC1 <- subset(seuratObj, seuratObj$sctype_classification == " Dendritic cells 1"| seuratObj$sctype_classification == "Migratory dendritic cells 2" | seuratObj$sctype_classification == "Proliferating DCs" |seuratObj$sctype_classification == "RBC" | seuratObj$sctype_classification == "Unknown")
ncol(seuratObjCDC1)

#active idents 
Idents(seuratObjCDC1) <- "sctype_classification"

PlotSeuratCDC1 <- DimPlot(seuratObjCDC1,)+ggtitle(paste0("Graph: ",FileName," Annotation CDC1s Before"))
PlotSeuratCDC1

```

## Checking Unknow cells
```{r}

# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjCDC1, expression = sctype_classification == "Unknown")
# Making a plot showcasing these genes
PlotUnknown <- FeaturePlot(subset(seuratObjCDC1, cells = unknown_cells),features = c("Cd81","Gcsam","Xcr1","Irf8"))
PlotUnknown1 <- PlotUnknown +plot_annotation(title = "Zooming on Unknown cluster: CDC1 Biomarkers")
PlotUnknown1 # ----> = CDC1

# Check RBC
# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjCDC1, expression = sctype_classification == "RBC")
# Making a plot showcasing these genes
PlotUnknown2 <- FeaturePlot(subset(seuratObjCDC1, cells = unknown_cells),features = c("Cd81","Gcsam","Xcr1","Irf8"))
PlotUnknown2 <- PlotUnknown2 +plot_annotation(title = "Zooming on RBC cluster: CDC1 Biomarkers")
PlotUnknown2 # -----> = CDC1

# Check Migratory CDC2 FOR Migratory CDC1
# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjCDC1, expression = sctype_classification == "Migratory dendritic cells 2")
# Making a plot showcasing these genes
PlotUnknown3 <- FeaturePlot(subset(seuratObjCDC1, cells = unknown_cells),features = c("Cd81","Gcsam","Laptm4b","Ncoa7","Ccr7"))
PlotUnknown3 <- PlotUnknown3 +plot_annotation(title = "Zooming on Migratory  CDC 2 cluster: Migratory CDC1 Biomarkers")
PlotUnknown3 # -----> = CDC1

# Check Migratory CDC2 FOR Migratory CDC2
# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjCDC1, expression = sctype_classification == "Migratory dendritic cells 2")
# Making a plot showcasing these genes
PlotUnknown4 <- FeaturePlot(subset(seuratObjCDC1, cells = unknown_cells),features = c("S100a4","Anxa3","Cdc42ep3","Ccr7"))
PlotUnknown4 <- PlotUnknown4 +plot_annotation(title = "Zooming in on Migratory  CDC 2 cluster: Migratory CDC2 Biomarkers")
PlotUnknown4 # -----> = CDC1

# Check Proliferating DCs FOR that they are all Proliferating DCs
# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjCDC1, expression = sctype_classification == "Proliferating DCs")
# Making a plot showcasing these genes
PlotUnknown5 <- FeaturePlot(subset(seuratObjCDC1, cells = unknown_cells),features = c("Mki67","Stmn1"))
PlotUnknown5 <- PlotUnknown5 +plot_annotation(title = "Zooming in on Migratory  CDC 2 cluster: Migratory CDC2 Biomarkers")
PlotUnknown5 # -----> = CDC1

```


## Manual Cluster slection Seurat Manier
```{r}
# Removing Second RBC cluster
# Removing part of the Migatory dendritic cells 2, To keep only the identified Migratory dendritic cells 1
# Rmoving far off cells
selected <- CellSelector(DimPlot(seuratObjCDC1))

```
##Remove CDC1 cells
```{r}
seuratObjCDC1 <- subset(seuratObjCDC1, cells = selected, invert=TRUE)

```


## Reasgin cells
```{r}

changecells <- WhichCells(seuratObjCDC1, expression = sctype_classification == "Migratory dendritic cells 2")
seuratObjCDC1$sctype_classification[changecells] <- "Migratory dendritic cells 1"

```

#Annontation Post-Processing of CDC1
```{r}

 PostAnnotClustCDC1 <- DimPlot(seuratObjCDC1, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle("CDC Final result")
 PostAnnotClustCDC1

```
# Final count of CDC1
```{r}
nCellsCDC1 <- ncol(seuratObjCDC1)
PlotCD1 <- data.frame(
  ObjectName= c("Seuratobj cell count" ,"Final seuratObjCDC1 cell count"),
  Cells = c(nCellsSeurat,nCellsCDC1)
)

BarplotCDC1 <- ggbarplot(
  PlotVBO,
  x = "ObjectName",
  y = "Cells",
  label = TRUE,
  fill = "ObjectName",
  palette = c("steelblue", "tomato"),
)+
scale_y_continuous(
    breaks = seq(0, 14000, by = 2000)
  )+ggtitle("Remainig CDC1 cell count after post-processing")

BarplotCDC1

```
 
## Notes
```{r}

blurb = paste("\n   Notes for The Post-Processing of SAM3.\n",
         " 
          Removed Cluster:
          
        Cluster 9: 89% -----> Removed
        Cluster 17: 89% -----> Removed
        Cluster11: Part selected 94% -- Removed
        
        Checked Unknown --> = CDC1
        Checked RBC part of CDC1 --> = CDC1
        Checked Migratory cells ---> Seperated Migratory DCs 1 and 2
        Checked Proliferating cells ---> Were correct
  ")
Notes <- ggplot() + 
  annotate("text", x = 4, y = 25, size=4, label = blurb) + 
  theme_void()
Notes

```

```{r}
#Saving Object
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))

saveRDS(seuratObj,paste0("SeuratObj_Post-Process_",FileName,".rds"))
saveRDS(seuratObjCDC1,paste0("SeuratObj_Post-Process_CDC1_",FileName,".rds"))

setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))
pdf(paste0("Graphs Post-Process_",FileName,".pdf"), width = 14,
  height = 10)

PlotSeurat 
#PlotSeuratR 
PostAnnotClust 
ClustRemoveMap1
ClustRemoveMap2
ClustRemoveMap3
PlotUnknown1
PlotUnknown2
PlotUnknown3
PlotUnknown4
PlotUnknown5
if (exists("PlotUnknown")) {print(PlotUnknown)}
PlotSeuratCDC1
PostAnnotClustCDC1
BarplotCDC1
Notes
dev.off()


```


