---
title: "Post-precossing"
output: html_document
---
##Functions
```{r}
colorSomeCells<-function(clusterMatrix, coordsTable, cellsToColor){
  clusterMatrix$toColor=FALSE
  clusterMatrix[cellsToColor,which(colnames(clusterMatrix)=="toColor")]<-TRUE
  
  p1 <- ggplot()+
    geom_point(aes_string(x=colnames(coordsTable)[1],y=colnames(coordsTable)[2], colour=clusterMatrix$toColor), data=coordsTable, size=1) +
    scale_color_manual(values=c('TRUE'="orangered",'FALSE'="lightgray")) +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.text=element_text(size=12))
  
  return(p1)
}

```



```{r}
## Packages
library("tidyverse")
library("Seurat")
library("SingleCellExperiment")
library("scater")
library("data.table")
library("ggpubr")
library("gridExtra")
library("fitdistrplus") 
library("dplyr")
library("plyr")
library("caret")
library("openxlsx")
library("ggplot2")
library("tibble")
library("scran")
library("limma")
library("ggrepel")
library("intrinsicDimension")
library("tidyr")
library("purrr")
library("ggrepel")
library("clustree")
library("limma")
library("patchwork")
library("future")
library('RColorBrewer')

```


#Post-Processing

After Basic filtering of data we want to take a closer look at each cluster that and see where further processing is necessary 


## Loading the Seurat Object
```{r}
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM06")
FileName <- basename(getwd())


#Loading Seaurat object
seuratObj <- readRDS(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Hashing/SeuratObj_HTO_",FileName,".rds"))



```


##Making Subsets of the data
```{r}

# Subset: Removing the Negative and Doublets
# Only HTO.data doublets removed ---> scdblfinder doublets are still in the the seuratObj 
ncol(seuratObj)
seuratObjR <- subset(seuratObj,seuratObj@meta.data$HTO_GUESS != "Doublet" & seuratObj@meta.data$HTO_GUESS != "Negative")
ncol(seuratObjR)

Idents(seuratObjR) <- "HTO_GUESS"

PlotSeurat <- DimPlot(seuratObj, label=T, repel=T )+ggtitle(paste0("Graph ",FileName))
PlotSeuratR <- DimPlot(seuratObjR, label=T, repel=T)+ggtitle(paste0("Graph",FileName))

PlotSeurat
PlotSeuratR 

Idents(seuratObjR) <- "seurat_clusters"

PlotSeuratRClust <- DimPlot(seuratObjR, label=T, repel=T )+ggtitle(paste0("Graph ",FileName," Clusters"))
PlotSeuratRClust

# ALL Doublets are removed

```



## Checking Unknow/ Suspicious cells
```{r}
# isolate Unknown cells
unknown_cells <- WhichCells(seuratObjR, expression = sctype_classification == " Basophil cell")
# Making a plot showcasing these genes

# Checking If its is Basophill Cells
PlotUnknown1 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Mcpt8","Fcer1a","Fcer1g","adt_CD49b"))
PlotUnknown1 <- PlotUnknown1 +plot_annotation(title = "Controling if Basophil cell")

# Chech if CDC1
PlotUnknown2 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Cd81","Gcsam","Xcr1","Irf8"))
PlotUnknown2 <- PlotUnknown2 +plot_annotation(title = "Controling if CDC1")

# Checking if its is CDC2
PlotUnknown3 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Sirpa","S100a4","Cd209a"))
PlotUnknown3 <- PlotUnknown3 +plot_annotation(title = "Controling if CDC2")

# Checking if Migratory CDC1 
PlotUnknown4 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Cd81","Gcsam","Laptm4b","Ncoa7","Ccr7"))
PlotUnknown4 <- PlotUnknown4 +plot_annotation(title = "Controling if Migartory CDC1")

# Checking if Plasmacytoid dendritic cells
PlotUnknown5 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Siglech","Tcf4","Ccr9","Bst2"))
PlotUnknown5 <- PlotUnknown5 +plot_annotation(title = "Controling if Plasmacytoid dendritic cells")

# Checking if Plasmacytoid dendritic cells
PlotUnknown6 <- FeaturePlot(subset(seuratObjR, cells = unknown_cells),features = c("Mki67","Stmn1"))
PlotUnknown6 <- PlotUnknown6 +plot_annotation(title = "Controling if Proliferating DCs")

PlotUnknown1
PlotUnknown2
PlotUnknown3
PlotUnknown4
PlotUnknown5
PlotUnknown6

# When looking at the feature plots No clear cell type is found for cluster 7, These are most likely not Basophills because of low to no experession of its bio markers. The cluster is also not CDC1,CDC2, Migratory CDC1,Plasmacytoid dendritic cells and Proliferating DCs because of low expressions of their biomarkes.

# When, having a further look at the MARKER RNA data it is found that the most top biomarkers have a low score and experession within the cluster. The only one that sticks out is CCR2 pointing to pre-CDC1

# To keep precedence between all samples this cluster will be removed when detected
```


## Manual Cluster selection of Whole cluster

Checking the Doublet count of Cluster 12/ Unknown cell type
Selection
```{r}
ClusterData <- seuratObj@meta.data
UMAPTable <-as.data.frame(seuratObj[['RNA_umap']]@cell.embeddings, stringsAsFactors = F)
#Color Cluster Number?
ColorIdent <- 7
wantedCells<-WhichCells(seuratObjR, idents = ColorIdent)
PrecentageDoublet <- (length(WhichCells(seuratObjR, expression = scDblFinder_class=="doublet", cells = wantedCells))/length(WhichCells(seuratObjR,wantedCells)))*100
PrecentageDoublet <- paste0(round(PrecentageDoublet,2),"%")
PrecentageDoublet
ClustRemoveMap1 <- colorSomeCells(ClusterData, UMAPTable, wantedCells)+ggtitle(paste0("Cluster ",ColorIdent, " = ",PrecentageDoublet," Doublets"))
ClustRemoveMap1

# Has a Almost no doublets
```


## Removing Selecetd cluster or cluster of choice

```{r}
# Remove Selected
#Remove specific cluster (Change idents to choose which cluster to remove)
 ClusterCellsRemove <- WhichCells(seuratObjR, idents = 7)
 seuratObjR <- subset(seuratObjR, cells = ClusterCellsRemove, invert=TRUE)

DimPlot(seuratObjR, reduction = "RNA_umap", label = T, repel = T, label.size = 4)

```






#Annontation Post-Processing of seuratObjR
```{r}
 PostAnnotClust <- DimPlot(seuratObj, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells Before"))

 PostAnnotClustR <- DimPlot(seuratObjR, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle(paste0("Graph: ",FileName," Annotation All cells After"))
 
 PostAnnotClust
 PostAnnotClustR

```


# CDC1: Repeat the process for CDC1
```{r}
#Subset: Only CDC 1

ncol(seuratObjR)
# Previous mistake in annotation excel ---> need the whitspace for CDC1
seuratObjCDC1 <- subset(seuratObjR, seuratObjR$sctype_classification == " Dendritic cells 1"| seuratObjR$sctype_classification == "Migratory dendritic cells 1" | seuratObjR$sctype_classification == "Proliferating DCs")
ncol(seuratObjCDC1)

#active idents 
Idents(seuratObjCDC1) <- "sctype_classification"

PlotSeuratCDC1 <- DimPlot(seuratObjCDC1,)+ggtitle(paste0("Graph: ",FileName," Annotation CDC1s Before"))
PlotSeuratCDC1

```


#Cleaning Up far off cells and removing Migratory CDC2
```{r}
selected <- CellSelector(DimPlot(seuratObjCDC1))
```

```{r}
seuratObjCDC1 <- subset(seuratObjCDC1, cells = selected, invert=TRUE)

```


##Annontation Post-Processing of CDC1
```{r}
# Migratory CDC1 still contain Migratory CDC2 but though to split apart
 PostAnnotClustCDC1 <- DimPlot(seuratObjCDC1, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')+ggtitle("CDC Final result")
 PostAnnotClustCDC1

```
 
# Notes
```{r}

blurb = paste("\n   Notes for The Post-Processing of SAM2.\n",
         "
		- Almost All Doublets removed when removing HTO.Data

    - Basophil cells ---> Low quality/ Pre-CDC1 ---> Removed
		
		- Migratory CDC1 already present")
Notes <- ggplot() + 
  annotate("text", x = 4, y = 25, size=4, label = blurb) + 
  theme_void()
Notes

```

#Saving Object
```{r}
#Saving Object
setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))

saveRDS(seuratObjR,paste0("SeuratObj_Post-Process_",FileName,".rds"))
saveRDS(seuratObjCDC1,paste0("SeuratObj_Post-Process_CDC1_",FileName,".rds"))

setwd(paste0("/Users/samue/Desktop/Stage VIB/Pre and Post processing Results/",FileName,"/Post-process/"))
pdf(paste0("Graphs Post-Process_",FileName,".pdf"), width = 14,
  height = 10)

PlotSeurat 
PlotSeuratR 
PostAnnotClust 
PostAnnotClustR
ClustRemoveMap1
PlotUnknown1
PlotUnknown2
PlotUnknown3
PlotUnknown4
PlotUnknown5
PlotUnknown6
if (exists("PlotUnknown")) {print(PlotUnknown)}
PlotSeuratCDC1
PostAnnotClustCDC1
Notes
dev.off()


```


