---
title: "Pre-processing"
output: html_document
---

Pre-processing of CITE-seq data This Script is the first and will be used to pre-process SAM2 Provided data

```{r}

###############################################
#LOADING PACKAGE
###############################################

library("renv")
library("tidyverse")
library("Seurat")
library("SingleCellExperiment")
library("scater") 
library("scran") # Note for Windows --> Bluster dependencie doesnt compile properly in windows, mannulay add the bluster package to library. Download ---> https://bioc.r-universe.dev/bluster
library('fields')
#library('modes') #Niet in CRan
library("dplyr")
library("stringr")
library("readr")
library("ggplot2")
library("HGNChelper") #For sc_type nesseacry

```

```{r}
#############################################
#RNA
############################################
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM2")
rawData <- Read10X("filtered_feature_bc_matrix")
rawDataRNA <- as.matrix(rawData$`Gene Expression`)
# Rawdata is 6.1 GB, it can be loaded but not examined ---> Took a subset of cells
rawDataRNA <- rawDataRNA[, 1:2000]

```

```{r}
sce<-SingleCellExperiment(list(counts=rawDataRNA))
# Everything starting with MT put in is.mito vector
is.mito <- grepl("^MT-", rownames(sce), ignore.case = TRUE)

#Scuttle function: addPerCellQC: Add QC metrics to a SummarizedExperiment
#QCmetric: Compute per-cell quality control metrics for a count matrix or a SingleCellExperiment. 

sce<- addPerCellQC(sce, subsets=list(Mito=is.mito))

# Make Metadata dataframe
metaData<-data.frame("staticNr"=colnames(rawDataRNA), 
                     "nGene"=sce$detected,
                     "nUMI"=sce$sum,
                     "percent.mito"=sce$subsets_Mito_percent, 
                     stringsAsFactors = F)
#Rownames fixen
rownames(metaData)<-metaData$staticNr
metaData$staticNr<-1


```

```{r}
# FILTERING Test

sampleName<-"GSM_2677817"
experiment <- sampleName
batch <- rep(sampleName, colnames(rawDataRNA) %>% length())

# Setting cut offs (Increased the cutoffs, Still Increase?)
# Nummber of genes
nmad_low_feature<-3
nmad_high_feature<-3

# Total counts all gene in a cell
nmad_low_UMI<-3
nmad_high_UMI<-3

# Precentage Mitchondrial gene
nmad_high_mito<-10

#Filter both Low and High outliers out
feature.drop.low <- isOutlier(sce$detected, nmads=nmad_low_feature, type="lower", log=TRUE,batch = batch)
feature.drop.high <- isOutlier(sce$detected, nmads=nmad_high_feature, type="higher", log=TRUE,batch = batch)
# Putting everything togheter
feature.drop<-as.logical(feature.drop.low + feature.drop.high,batch = batch)

#Filter both Low and High outliers out
libsize.drop.low <- isOutlier(sce$sum, nmads=nmad_low_UMI, type="lower", log=TRUE,batch = batch)
libsize.drop.high <- isOutlier(sce$sum, nmads=nmad_high_UMI, type="higher", log=TRUE,batch = batch)

# Putting everything togheter
libsize.drop<-as.logical(libsize.drop.low+libsize.drop.high)

#Filtering High out
mito.drop.high <- isOutlier(sce$subsets_Mito_percent, nmads=nmad_high_mito, type="higher",batch = batch)
mito.drop <- as.logical(mito.drop.high)


# Add dropped cells to metadata
metaData$nGene.drop=feature.drop
metaData$nUMI.drop=libsize.drop
metaData$mito.drop=mito.drop
metaData$final.drop=feature.drop | libsize.drop | mito.drop

#Removing the outliers
#The filted data is put in a seprate object
scef <- sce[,!(libsize.drop | feature.drop | mito.drop)]

# Creating a Filter Metadata for the plots
metaDataF<-data.frame("staticNr"=colnames(scef),
                     "nGene"=scef$detected,
                     "nUMI"=scef$sum,
                     "percent.mito"=scef$subsets_Mito_percent, 
                     stringsAsFactors = F)
rownames(metaDataF)<-metaDataF$staticNr
metaDataF$staticNr<-1

# Defining the cutoffs
ul.mito <- attr(mito.drop.high,'thresholds')[2]
ll.cd <- attr(libsize.drop.low,'thresholds')[1]
ul.cd <- attr(libsize.drop.high,'thresholds')[2]
ll.ng <- attr(feature.drop.low,'thresholds')[1]
ul.ng <- attr(feature.drop.high,'thresholds')[2]
```

#Graphs Before and after

Graph of data Before and After Filtering Here we make a scatter, histogram and violin plot of the data before and after its gets filtered (Note: Verbeter look van grafieken)

```{r}

MitoPrecentage <- sce$subsets_Mito_percent

sctplt1 <- ggplot(metaData,aes(x=nUMI, y=nGene)) + 
  geom_point(aes(colour = MitoPrecentage ))+
  scale_colour_gradientn(colours=terrain.colors(10))+
  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.5)+
geom_hline(yintercept = ll.ng,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_hline(yintercept = ul.ng,linetype="dotted", 
                color = "red", size=1.5)+
    theme_bw()

MitoPrecentageF <- scef$subsets_Mito_percent

sctplt2 <- ggplot(metaDataF,aes(x=nUMI, y=nGene)) + 
  geom_point(aes(colour = MitoPrecentageF ))+
  scale_colour_gradientn(colours=terrain.colors(10))+
  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.5)+
geom_hline(yintercept = ll.ng,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_hline(yintercept = ul.ng,linetype="dotted", 
                color = "red", size=1.5)+
  theme_bw()

sctplt1 
sctplt2
#Violin and Histogram plot VOor en NA
```

```{r}
hist1 <- ggplot(metaData, aes(x = nUMI)) +
  geom_histogram(binwidth=100)+  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.1)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.1)+
  theme_bw()

hist2 <- ggplot(metaDataF, aes(x = nUMI)) +
  geom_histogram(binwidth=100)+
    geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.1)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.1)+
  theme_bw()+

hist1 
hist2

```

```{r}

vlplt1 <- ggplot(metaData,aes(x=nUMI, y=nGene)) + 
  geom_violin(fill="red")+
  theme_bw()

vlplt2 <-ggplot(metaDataF,aes(x=nUMI, y=nGene)) + 
  geom_violin(fill= "green")+
  theme_bw()

vlplt1 + vlplt2
```

##Creating Seurat Object

```{r}
rawDataFiltered<-rawDataRNA[rownames(scef),colnames(scef)] 
# IETS FOUT GEGAAN HIER
# CREATE SEURAT OBJECT
cells.to.keep <- colnames(scef)
seuratObj <- CreateSeuratObject(rawDataFiltered, project = experiment)


```

##Normailzation

```{r}
#Creating Seurat Object
seuratObj <- FindVariableFeatures(seuratObj, selection.method = 'vst', nfeatures = 2000)

 seuratObj <- NormalizeData(seuratObj, normalization.method = "LogNormalize", scale.factor = 1e4)

```

##Dimensional reduction

```{r}

all.genes <- rownames(seuratObj)
seuratObj <- ScaleData(seuratObj, features = all.genes)

seuratObj <- RunPCA(seuratObj, 
                    features = VariableFeatures(object = seuratObj), 
                    ndims.print = 1:5, nfeatures.print = 10,
                    assay = "RNA",
                    reduction.name = "RNA_pca",
                    reduction.key = "rnaPC_")
```

## Optimize PCA

```{r}

ElbowPlot(seuratObj, reduction = "RNA_pca")

# Results SAM2: Use 14 Dimension
```

```{r}

print(seuratObj[["RNA_pca"]], dims = 1:5, nfeatures = 5)


```

##Clustering of cells

```{r}
# Test more than 14 dimensions (see example script)
seuratObj <- FindNeighbors(seuratObj, dims = 1:14, reduction = "RNA_pca")
seuratObj <- FindClusters(seuratObj, resolution = 0.5)

```

##UMAP

```{r}

seuratObj <- RunUMAP(seuratObj, dims = 1:14,reduction = "RNA_pca", reduction.name = "RNA_umap" )
DimPlot(seuratObj, reduction = "RNA_umap")
```

##Finding Cluster Biomarkers

```{r}

ClusterRNA6 <- FindAllMarkers(seuratObj, only.pos = TRUE)
ClusterRNA6<-ClusterRNA6[order(ClusterRNA6$p_val_adj, decreasing = FALSE), ]
head(ClusterRNA6, n = 6)


```

## Plotting Biomarkers

```{r}

FeaturePlot(seuratObj, features = c("Ncr1", "Cacnb3", "Pclaf", "Spc24", "Cd3g", "Cdk1"))

```


#ADT

```{r}
rawDataADT <- as.matrix(rawData$`Antibody Capture`)
rawDataADT <- rawDataADT[, 1:2000]

raw.names <- rownames(rawDataADT)
cells.use  <- intersect(colnames(rawDataADT), colnames(seuratObj))
ABS.use  <- rownames(rawDataADT)
rawDataADT <- rawDataADT[ABS.use, cells.use]
seuratObj[["ADT"]] <- CreateAssayObject(counts = rawDataADT[,colnames(seuratObj)])

#Normalization
seuratObj <- NormalizeData(seuratObj, assay = "ADT", normalization.method = "CLR", verbose=T)

seuratObj <- FindVariableFeatures(seuratObj,assay="ADT",selection.method = "vst", nfeatures=nrow(rawDataADT))


#Dimensenioanly Reduction
seuratObj <- ScaleData(seuratObj, assay = "ADT")

seuratObj <- RunPCA(seuratObj, 
                    features = VariableFeatures(object = seuratObj, assay = "ADT"), 
                    ndims.print = 1:5, nfeatures.print = 10,
                    assay = "ADT",
                    reduction.name = "ADT_pca",
                    reduction.key = "adtPC_")
# Finding Cluster

seuratObj <- FindNeighbors(seuratObj, reduction = "ADT_pca",dims = 1:14)
seuratObj <- FindClusters(seuratObj, resolution = 0.5)


# UMAP
seuratObj <- RunUMAP(seuratObj, dims = 1:14, assay = "ADT", reduction = "ADT_pca", reduction.name ="ADT_umap" )
DimPlot(seuratObj, reduction = "ADT_umap")

#Finding Markers

ClusterADT6 <- FindAllMarkers(seuratObj, only.pos = TRUE, assay = "ADT")
head(ClusterADT6, n = 6)

FeaturePlot(seuratObj, features = c("CD24", "CD9", "CD371	", "CD272", "XCR1", "CD29"))

```
#Annotation Cells

```{r}

## readRDS of your sample before
# sample <- readRDS("/absolute/path/sample.RDS");
source("https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/R/sctype_wrapper.R"); 
seuratObj <- run_sctype(seurat_object = seuratObj,
                     assay = "RNA",
                     scaled = TRUE,
                     known_tissue_type="Immune system",
                     custom_marker_file="/Users/samue/Desktop/Stage VIB/CDC Annotatie.xlsx",
                     name="sctype_classification")

# MARKERS: General CDC
# MARKERS: CDC1 and 2 , Migetory and Profilatrate

DimPlot(seuratObj, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')        
```



