---
title: "Pre-processing"
output: html_document
---

Pre-processing of CITE-seq data This Script is the first and will be used to pre-process SAM2 Provided data

```{r}

###############################################
#LOADING PACKAGE
###############################################

library("renv")
#library("clustree")
library("tidyverse")
library("Seurat")
library("SingleCellExperiment")
library("scater") 
library("scran") # Note for Windows --> Bluster dependencie doesnt compile properly in windows, mannulay add the bluster package to library. Download ---> https://bioc.r-universe.dev/bluster
library('fields')
library("dplyr")
library("stringr")
library("readr")
library("ggplot2")
library("HGNChelper") #For sc_type nesseacry
library("scDblFinder")
library("readxl")
library("patchwork")
```

```{r}
#############################################
#RNA
############################################
setwd("/Users/samue/Desktop/Stage VIB/RawData/SAM2")
rawData <- Read10X("filtered_feature_bc_matrix")
rawDataRNA <- as.matrix(rawData$`Gene Expression`)
# Rawdata is 6.1 GB, it can be loaded but not examined ---> Took a subset of cells
rawDataRNA <- rawDataRNA[, 1:2000]

```

```{r}
sce<-SingleCellExperiment(list(counts=rawDataRNA))
# Everything starting with MT put in is.mito vector
is.mito <- grepl("^MT-", rownames(sce), ignore.case = TRUE)

#Scuttle function: addPerCellQC: Add QC metrics to a SummarizedExperiment
#QCmetric: Compute per-cell quality control metrics for a count matrix or a SingleCellExperiment. 

sce<- addPerCellQC(sce, subsets=list(Mito=is.mito))

# Make Metadata dataframe
metaData<-data.frame("staticNr"=colnames(rawDataRNA), 
                     "nGene"=sce$detected,
                     "nUMI"=sce$sum,
                     "percent.mito"=sce$subsets_Mito_percent, 
                     stringsAsFactors = F)
#Rownames fixen
rownames(metaData)<-metaData$staticNr
metaData$staticNr<-1


```

```{r}
# FILTERING Test

sampleName<-"GSM_2677817"
experiment <- sampleName
batch <- rep(sampleName, colnames(rawDataRNA) %>% length())

# Setting cut offs (Increased the cutoffs, Still Increase?)
# Nummber of genes
nmad_low_feature<-3
nmad_high_feature<-3

# Total counts all gene in a cell
nmad_low_UMI<-3
nmad_high_UMI<-3

# Precentage Mitchondrial gene
nmad_high_mito<- 5

#Filter both Low and High outliers out
feature.drop.low <- isOutlier(sce$detected, nmads=nmad_low_feature, type="lower", log=TRUE,batch = batch)
feature.drop.high <- isOutlier(sce$detected, nmads=nmad_high_feature, type="higher", log=TRUE,batch = batch)
# Putting everything togheter
feature.drop<-as.logical(feature.drop.low + feature.drop.high,batch = batch)

#Filter both Low and High outliers out
libsize.drop.low <- isOutlier(sce$sum, nmads=nmad_low_UMI, type="lower", log=TRUE,batch = batch)
libsize.drop.high <- isOutlier(sce$sum, nmads=nmad_high_UMI, type="higher", log=TRUE,batch = batch)

# Putting everything togheter
libsize.drop<-as.logical(libsize.drop.low+libsize.drop.high)

#Filtering High out
mito.drop.high <- isOutlier(sce$subsets_Mito_percent, nmads=nmad_high_mito, type="higher",batch = batch)
mito.drop <- as.logical(mito.drop.high)


# Add dropped cells to metadata
metaData$nGene.drop=feature.drop
metaData$nUMI.drop=libsize.drop
metaData$mito.drop=mito.drop
metaData$final.drop=feature.drop | libsize.drop | mito.drop

#Removing the outliers
#The filted data is put in a seprate object
scef <- sce[,!(libsize.drop | feature.drop | mito.drop)]

# Creating a Filter Metadata for the plots
metaDataF<-data.frame("staticNr"=colnames(scef),
                     "nGene"=scef$detected,
                     "nUMI"=scef$sum,
                     "percent.mito"=scef$subsets_Mito_percent, 
                     stringsAsFactors = F)
rownames(metaDataF)<-metaDataF$staticNr
metaDataF$staticNr<-1

# Defining the cutoffs
ul.mito <- attr(mito.drop.high,'thresholds')[2]
ll.cd <- attr(libsize.drop.low,'thresholds')[1]
ul.cd <- attr(libsize.drop.high,'thresholds')[2]
ll.ng <- attr(feature.drop.low,'thresholds')[1]
ul.ng <- attr(feature.drop.high,'thresholds')[2]
```

#Graphs Before and after

Graph of data Before and After Filtering Here we make a scatter, histogram and violin plot of the data before and after its gets filtered (Note: Verbeter look van grafieken)

```{r}

MitoPrecentage <- sce$subsets_Mito_percent

sctplt1 <- ggplot(metaData,aes(x=nUMI, y=nGene)) + 
  geom_point(aes(colour = MitoPrecentage ))+
  scale_colour_gradientn(colours=terrain.colors(10), limits=c(0,4))+
  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.5)+
geom_hline(yintercept = ll.ng,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_hline(yintercept = ul.ng,linetype="dotted", 
                color = "red", size=1.5)+
    theme_bw()

MitoPrecentageF <- scef$subsets_Mito_percent

sctplt2 <- ggplot(metaDataF,aes(x=nUMI, y=nGene)) + 
  geom_point(aes(colour = MitoPrecentageF ))+
  scale_colour_gradientn(colours=terrain.colors(10))+
  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.5)+
geom_hline(yintercept = ll.ng,linetype="dotted", 
                color = "blue", size=1.5)+
   geom_hline(yintercept = ul.ng,linetype="dotted", 
                color = "red", size=1.5)+
  theme_bw()

sctplt1 
sctplt2

# Zoomed in Plots
sctplt1+ coord_cartesian(ylim = c(0, 2500),xlim = c(0,2500))
sctplt2+ coord_cartesian(ylim = c(0, 2500),xlim = c(0,2500))

```

```{r}
hist1 <- ggplot(metaData, aes(x = nUMI)) +
  geom_histogram(binwidth=100)+  
  geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.1)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.1)+
  theme_bw()

hist2 <- ggplot(metaDataF, aes(x = nUMI)) +
  geom_histogram(binwidth=100)+
    geom_vline(xintercept = ll.cd,linetype="dotted", 
                color = "blue", size=1.1)+
   geom_vline(xintercept = ul.cd,linetype="dotted", 
                color = "red", size=1.1)+
  theme_bw()+

hist1 
hist2

```

```{r}

vlplt1 <- ggplot(metaData,aes(x=nUMI, y=nGene)) + 
  geom_violin(fill="red")+
  theme_bw()

vlplt2 <-ggplot(metaDataF,aes(x=nUMI, y=nGene)) + 
  geom_violin(fill= "green")+
  theme_bw()

vlplt1 + vlplt2
```

## Mitochondrial gene Percentage plot
```{r}
Mito1 <- ggplot(metaData, aes(x=MitoPrecentage)) + 
  geom_histogram(binwidth = 0.1)+
  geom_vline(xintercept = ul.mito,linetype="dotted", 
                color = "blue", size=1.5)

Mito2 <- ggplot(metaDataF, aes(x=MitoPrecentageF)) + 
  geom_histogram(binwidth = 0.1)+
  geom_vline(xintercept = ul.mito,linetype="dotted", 
                color = "blue", size=1.5)

Mito1
Mito2

# Zoom in grafiek 1
Mito1 + coord_cartesian(xlim = c(0,10))




```


##How many cells were removed during filtering?
```{r}
BeforeFiltering <- ncol(sce)
AfterFilering <- ncol(scef)
#AfterscDbl <-  table(scef$scDblFinder.class)

print("How many cells removed?")
print(paste("Before Filtering",BeforeFiltering))
print(paste("After Filtering",AfterFilering))
#print(paste("After scDblFinder:"))
#AfterscDbl



```


##Creating Seurat Object

```{r}
rawDataFiltered<-rawDataRNA[rownames(scef),colnames(scef)]
# Creating ADT RawData
rawDataADT <- as.matrix(rawData$`Antibody Capture`)
rawDataADT <- rawDataADT

rm(rawData)
rm(rawDataRNA)
rm(sce)
gc()

# CREATE SEURAT OBJECT
cells.to.keep <- colnames(scef)
seuratObj <- CreateSeuratObject(rawDataFiltered, project = experiment, min.cells=1)

#Adding scDblFinder data to the Seuratobject
#seuratObj$scDblFinder.score <- scef$scDblFinder.score
#seuratObj$scDblFinder.class <- scef$scDblFinder.class

# Removing Object for performance
rm(rawDataFiltered)
rm(scef)
gc()


```

##Normailzation

```{r}
#Creating Seurat Object
seuratObj <- FindVariableFeatures(seuratObj, selection.method = 'vst', nfeatures = 2000)

 seuratObj <- NormalizeData(seuratObj, normalization.method = "LogNormalize", scale.factor = 1e4)

```

##Dimensional reduction

```{r}

all.genes <- rownames(seuratObj)
seuratObj <- ScaleData(seuratObj, features = all.genes)

#seuratObj <- wilcoxauc(seuratObj, 'cell_type', seurat_assay = 'RNA') # Presto not in CRAN, Recieve error when using recommend command devtools::install_github("immunogenomics/presto")

seuratObj <- RunPCA(seuratObj, 
                    features = VariableFeatures(object = seuratObj), 
                    ndims.print = 1:5, nfeatures.print = 10,
                    assay = "RNA",
                    reduction.name = "RNA_pca",
                    reduction.key = "rnaPC_")
```

## Optimize PCA

```{r}

ElbowPlot(seuratObj, reduction = "RNA_pca")

# Results SAM2: Use 14 Dimension
```

```{r}

print(seuratObj[["RNA_pca"]], dims = 1:5, nfeatures = 5)


```

##Finding Best Dimension Clustering of cells

```{r}
# Test more than 14 dimensions (see example script)
StartingDims <- 4 # Always do Starting Amount of Dims - 1
EndingDims <- 14
TotalDims <- EndingDims - StartingDims

print(paste0("Working on Dims Starting form ",StartingDims, " to Dims ", EndingDims ," Total: ",TotalDims))

ListDims <- seq(1:TotalDims+1)
for(i in ListDims){
  #Creating Mulitple Cluster Maps with Different Dims
  StartingDims <- StartingDims + 1
  seuratObj <- FindNeighbors(seuratObj, dims = 1:StartingDims, reduction = "RNA_pca")
  seuratObj <- FindClusters(seuratObj, resolution = 0.5)
  seuratObj <- RunUMAP(seuratObj, dims = 1:StartingDims,reduction = "RNA_pca", reduction.name = "RNA_umap" )
  
  #Title for UMap
  UMAPTitle <- paste0("UMAP Number = ",StartingDims)
  UMAPgraph  <-DimPlot(seuratObj, reduction = "RNA_umap")+ggtitle(UMAPTitle)
  print(UMAPgraph)
}
```
## Loop For best Resolution of the found dims

# Best Clustering of cells
```{r}

seuratObj <- FindNeighbors(seuratObj, dims = 1:14, reduction = "RNA_pca")
  seuratObj <- FindClusters(seuratObj, resolution = 0.5)
  seuratObj <- RunUMAP(seuratObj, dims = 1:14,reduction = "RNA_pca", reduction.name = "RNA_umap" )
  DimPlot(seuratObj, reduction = "RNA_umap")
```

##Finding Cluster Biomarkers

```{r}

ClusterRNA <- FindAllMarkers(seuratObj, only.pos = TRUE)
ClusterRNA<-ClusterRNA[order(ClusterRNA$p_val_adj, decreasing = FALSE), ]
head(ClusterRNA, n = 6)


```

## Plotting Biomarkers

```{r}

FeaturePlot(seuratObj, features = c("Ncr1", "Cacnb3", "Pclaf", "Spc24", "Cd3g", "Cdk1"))

```


#ADT

```{r}

raw.names <- rownames(rawDataADT)
cells.use  <- intersect(colnames(rawDataADT), colnames(seuratObj))
ABS.use  <- rownames(rawDataADT)
rawDataADT <- rawDataADT[ABS.use, cells.use]
seuratObj[["ADT"]] <- CreateAssayObject(counts = rawDataADT[,colnames(seuratObj)])

#Normalization
seuratObj <- NormalizeData(seuratObj, assay = "ADT", normalization.method = "CLR", verbose=T)

seuratObj <- FindVariableFeatures(seuratObj,assay="ADT",selection.method = "vst", nfeatures=nrow(rawDataADT))


#Dimensenioanly Reduction
seuratObj <- ScaleData(seuratObj, assay = "ADT")

seuratObj <- RunPCA(seuratObj, 
                    features = VariableFeatures(object = seuratObj, assay = "ADT"), 
                    ndims.print = 1:5, nfeatures.print = 10,
                    assay = "ADT",
                    reduction.name = "ADT_pca",
                    reduction.key = "adtPC_")
# Finding Cluster

StartingDimsADT <- 4 # Always do Starting Amount of Dims - 1
EndingDimsADT <- 14
TotalDimsADT <- EndingDimsADT - StartingDimsADT

print(paste0("Working on Dims Starting form ",StartingDimsADT, " to Dims ", EndingDimsADT ," Total: ",TotalDimsADT))

ListDimsADT <- seq(1:TotalDimsADT+1)
for(i in ListDimsADT){
  #Creating Mulitple Cluster Maps with Different Dims
  StartingDimsADT <- StartingDimsADT + 1
  seuratObj <- FindNeighbors(seuratObj, dims = 1:StartingDimsADT, reduction = "ADT_pca")
  seuratObj <- FindClusters(seuratObj, resolution = 0.5)
  seuratObj <- RunUMAP(seuratObj, dims = 1:StartingDimsADT,reduction = "ADT_pca", reduction.name = "ADT_umap" )
  
  #Title for UMap
  UMAPTitleADT <- paste0("UMAP Number = ",StartingDimsADT)
  UMAPgraphADT  <-DimPlot(seuratObj, reduction = "ADT_umap")+ggtitle(UMAPTitleADT)
  print(UMAPgraphADT)
}


#Best Cluster (Change dims)
seuratObj <- FindNeighbors(seuratObj, reduction = "ADT_pca",dims = 1:14)
seuratObj <- FindClusters(seuratObj, resolution = 0.5)


# UMAP
seuratObj <- RunUMAP(seuratObj, dims = 1:14, assay = "ADT", reduction = "ADT_pca", reduction.name ="ADT_umap" )
DimPlot(seuratObj, reduction = "ADT_umap")

#Finding Markers

ClusterADT6 <- FindAllMarkers(seuratObj, only.pos = TRUE, assay = "ADT")
head(ClusterADT6, n = 6)

FeaturePlot(seuratObj, features = c("CD24", "CD9", "CD371	", "CD272", "XCR1", "CD29"))

```



#Annotation Cells

```{r}

## readRDS of your sample before
# sample <- readRDS("/absolute/path/sample.RDS");
source("https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/R/sctype_wrapper.R"); 
seuratObj <- run_sctype(seurat_object = seuratObj,
                     assay = "RNA",
                     scaled = TRUE,
                     known_tissue_type="Immune system",
                     custom_marker_file="/Users/samue/Desktop/Stage VIB/CDC Annotatie.xlsx",
                     name="sctype_classification")

# MARKERS: General CDC
# MARKERS: CDC1 and 2 , Migetory and Profilatrate

DimPlot(seuratObj, reduction = "RNA_umap", label = TRUE, repel = TRUE, group.by = 'sctype_classification')        
```


# After Clustering Filitering (see notes and scripts (general))
```{r}
# Top Markers per Cluster
totalNrClusters<-max(as.numeric(names(table(ClusterRNA$cluster))))
BioMarkerList <- list()

for(i in 1:totalNrClusters){
  tmp <- ClusterRNA[ClusterRNA$cluster==i,]
  tmp$score<-tmp$pct.1/(tmp$pct.2+0.01)*tmp$avg_log2FC
  BioMarkerList[[i]]<-tmp[order(tmp$score, decreasing=TRUE),] #Already sorted by score
  TopMarkersperCluster <- list(head(BioMarkerList[[i]]$gene))
  print(paste("Top Markers of Cluster:",i,"=", TopMarkersperCluster))
}

#tmp$score<-tmp$pct.1/(tmp$pct.2+0.01)*tmp$avg_log2FC?? Score voor biomarkers
# Sort by Frequencie?

```

## Finding Doublets
```{r}
# Make Seuratobject a SingleCellExpirment Object
Doublets <- as.SingleCellExperiment(seuratObj)
Doublets$seurat_cluster <- seuratObj$seurat_clusters

# Find the Doublets
Doublets <- scDblFinder(Doublets, clusters="seurat_cluster") 

#Doublets per Cluster
#dbl <- findDoubletClusters(counts(Doublets), Doublets$seurat_cluster)

# Work within Seuratobject to compare cluster to scDblFinder.class

# Add to the Orginal SeuratObject
seuratObj$scDblFinder_class <- Doublets$scDblFinder.class
seuratObj$scDblFinder_score <- Doublets$scDblFinder.score


cellsNames <- droplevels(seuratObj$seurat_clusters)
TrueDoubles <- seuratObj$scDblFinder_class


ClusterDoublets <- as.data.frame(
  table(cellsNames[TrueDoubles == "doublet"])
)

AfterscDbl <-table(seuratObj$scDblFinder_class)
print(paste("After scDblFinder:"))
AfterscDbl
ClusterDoublets
# Remove Created object
rm(Doublets)
gc()

```


## Control if Mitochondrian gene Precentage for each gene
```{r}
#Empty Vector
PlotPercentageMito<- c()


for (i in 1:totalNrClusters){
  TotalGenePerCluster <- length(BioMarkerList[[i]]$gene)
  is.mito.per.Cluster <- grepl("^MT-", rownames(BioMarkerList[[i]]), ignore.case = TRUE)
  PrecentageMitoPerCluster <- round((sum(is.mito.per.Cluster)/TotalGenePerCluster)*100,digits = 3)
  
  # To keep all the numbers for the plot
  PlotPercentageMito <- c(PlotPercentageMito,PrecentageMitoPerCluster)

  print(paste("Cluster",i,"Precentage Mitchondriale =",PrecentageMitoPerCluster))
}
#Ploting the data
ClusterMitoPerPlot <- data.frame(Cluster = seq(1:totalNrClusters),
                                 PercentageMito=PlotPercentageMito)
  
  ggplot(ClusterMitoPerPlot, aes(x=Cluster, y = PercentageMito)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
    labs(
      title = "Percentage Mitochondrian genes per Cluster",
      x = "Cluster",
      y = "Percentage Mitochondrian (%)"
    )


# Goei Cutoffs for Mito gene Precentage --> 10%?
# Show on the plot (Aantonen als mit gene geconcentreed zijn)
```

##Cluster ADT count
```{r}
PlotPercentageADT <- c()

for (i in 1:totalNrClusters){
  
  TotalADTPerCluster <- length(ClusterADT6$gene[ClusterADT6$cluster==i])
  TotalGenePerCluster <- length(BioMarkerList[[i]]$cluster)
  
  # Divede the ADT count with the total gene count per cluster and round to 3 digits
  PrecentageADT <- round((sum(TotalADTPerCluster)/TotalGenePerCluster)*100,digits = 3)
  
  # To keep all the numbers for the plot
  PlotPercentageADT <- c(PlotPercentageADT,PrecentageADT)
  
  print(paste("Cluster",i,"Precentage ADT count compared to Cluster count =",PrecentageADT))
}

#Ploting the data
ClusterADTPPerPlot <- data.frame(Cluster = seq(1:totalNrClusters),
                                 PercentageADT=PlotPercentageADT)
  
  ggplot(ClusterADTPPerPlot, aes(x= Cluster ,y = PercentageADT)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
    labs(
      title = "Percentage ADT per Cluster",
      x = "Cluster",
      y = "Percentage ADT (%)"
    )


# Good Cutoffs also 10%?
# Ploten on RNA_UMAP and ADT_UMAP
```

## Diagnostic Plots

```{r}



```


# Add Manual Clustering (Remove the markers out of excel and shown manually) (Automatisch uit excel halen)

```{r}
AnnotData <- read_xlsx(path = "/Users/samue/Desktop/Stage VIB/CDC Annotatie.xlsx")
AnnotData

plot_list <- list()

for (i in 1:nrow(AnnotData)){
  
  ExcelMarker <- unlist(strsplit(AnnotData$geneSymbolmore1[row.names(AnnotData)==i],","))
  #Have To split it up because FeaturePlot see list of genes as 1 name
  
  AnnotTitle <- AnnotData$cellName[row.names(AnnotData)==i]
  
  # Featureplot best used for looking per gene
  print(AnnotTitle)
  
  p <- FeaturePlot(object = seuratObj, features = ExcelMarker, cols = c("grey", "blue"), 
            reduction = "RNA_umap", min.cutoff = 'q2', max.cutoff = 'q98', pt.size = 1.5)
  
  p_combined <- wrap_plots(p, ncol=2) + plot_annotation(title = AnnotTitle)
  
  plot_list[[i]] <- p_combined
  
  print(plot_list[[i]])
   
  }

ExcelMarker
# Look for Seurat Function Module to bring all gene togheter in 1 plot

```


